\documentclass[a4paper,10pt]{article}
\usepackage{kusochek}
\usepackage{eucal}
\usepackage{xcolor}
\usepackage{bm}

\begin{document}
\title{Curvature tensor of smoothable Alexandrov spaces.}
\author{LP}
\maketitle

\tableofcontents

\newcommand{\M}{\mathcal M} 
\newcommand{\A}{\mathcal A} 
\newcommand{\SMA}{\mathcal{SMA}} 
\newcommand{\SAA}{\mathcal{SAA}} 
\newcommand{\ccto}{\stackrel{C^1_{Alex}}{\longrightarrow}}
\newcommand{\cto}{\stackrel{C}{\longrightarrow}}
\newcommand{\x}{\mathfrak x}
\newcommand{\X}{\mathfrak X}

\section{Introduction}
\subsection{Main result and corollaries}

By Alexandrov space we  mean ``finite dimensional Alexandrov space with curvature bounded   below''. 
By Riemannian manifold we  mean complete Riemannian manifold. 

We consider here an important class of 
 Alexandrov spaces, namely, limits of Riemannian manifolds. We call such spaces smoothable:
\begin{rdef}{Definition} An $m$-dimensional Alexandrov space $A$ is called \emph{smoothable}
if it can be presented as a Gromov--Hausdorff limit by a non-collapsing sequence of Riemannian manifolds $M_n$ with $\sec M_n\ge\kappa$ for some fixed $\kappa\in\RR$ (here, $\sec$ denotes sectional curvature).



Given a smoothable Alexandrov space $A$,
a sequence of Riemannian manifolds $M_n$ as above
together with a sequence of approximations $a_n\:M_n\to A$
will be called \emph{smoothing} of $A$
(briefly $M_n\smooths{} A$, or $M_n\smooths{a_n} A$).
\end{rdef}

\begin{rdef}{Remarks}
\begin{itemize}
\item
It follows from Perelman stability theorem (see \cite{PerStab}, \cite{KapStab})
that for sufficiently large $n$  we can take approximations
to be homeomorphisms $a_n^{hom}: M_n\to A$.
\item
In particular this implies that smoothable Alexanrdov space is a complete
metric manifold without boundary.

\end{itemize}
\end{rdef}

In this paper we introduce a notion of a curvature tensor for 
smoothable Alexandrov spaces, our main result is \ref{main}.
However
the invariant description of 
a curvature as a
 "measure valued tensor"
 requires a number of technical definitions
( in particular we need 
 an analog of tensor calculus for Alexandrov spaces).
In this section we formulate the main
result in a different way, using the following curvature description:

\begin{rdef}{Definition}
Let $M$ be an $m$-dimensional
manifold. For
a point $p\in M$ and vectors
$v_1,\dots, v_{m-2}\in T_pM$
we define a
\emph{co-sectional curvature} 
by the formula
$$K^M(v_1\wedge\dots\wedge v_{m-2})=|v_1\wedge\dots\wedge v_{m-2}|^2\cdot K_\sigma,$$
where
$K_\sigma$ is the sectional curvature of $M$ at $p$ on
the plane orthogonal to 
$v_1,\dots, v_{m-2}$.

\end{rdef}
We need
an analog of $C^1$-convergent sequence
of functions
for Alexandrov spaces -
Alexandrov smooth
(?) test sequence of functions (see Definition~\ref{}).

\begin{thm}{Main theorem - light edition}
Let  $A$  be a smoothable Alexandrov space with homeomorphism
 approximations
$M_n\smooths{a_n^{hom}} A$. Let
 $f^1_n\to f^1,\dots,f^{m-2}_n\to f^{m-2}$
 be arbitrary
 $(m-2)$-collection of
 test sequences. 
 %We associate with this collection a sequence of functions $k_n: M_n\to \R$ defined by
 %$$k_n=|\nabla f^1\wedge\dots\wedge\nabla f^{m-2}_n|^2\cdot  K^{\nabla f^1\wedge\dots\wedge\nabla f^{m-2}_n}({M_n})$$
Then \linebreak
$a_n^{hom}\# K^{M_n}({\nabla f^1_n\wedge\dots\wedge\nabla f^{m-2}_n})$ weakly converges to some measure $k$ on $A$ (here $\#$ is a push forward of measures).

\end{thm}



\medskip


Let us state some corollaries of the main theorem \ref{main}.

In case when the limit space is a compact Riemannian mainfold the situation is simpler,
as one can see from the following formulation.

\begin{thm}{Corollary}{\bf ?!!!AP}
Assume $M_n\smooths{} M$ and $M=(M,g)$ is a compact Riemannian manifold.
Then for all large $n$,
one can choose diffeomorphisms ({\bf ?!!!}) $f_n\:M\to M_n$,
so that the Riemannian metric $g_n$ induced by $f_n$ on $M$ converges to $g$.
Moreîver, given smooth vector fields $X,Y,Z,T$ on $M$, the functions $g_n(R_n(X,Y)Z,T)$ weakly converge to $g(R(X,Y)Z,T)$.
\end{thm}
In particular,
if $M$ is a Riemannian manifold,
$M_n\smooths{} M$,
and for each $n$ the curvature tensor at each point of $M_n$
belong to a convex $\op{SO}(m)$-symmetric set $Q$ of curvature tensors
then curvature tensor of $M$ belongs to $Q$ pointwise.
(For example, one could take $Q$ to be the set of positive curvature operators.)

\begin{thm}{Corollary}\label{CorSc}

 Let we have smoothing via homeomorphisms $M_n\smooths{a_n^{hom}} A$.
Then $a_n^{hom}\#\Sc_{M_n}$ weakly converge to some measure $\mu$ on $A$.
(Here, $\Sc$ denotes scalar curvature
and $\#$ stays for pushforward of measures.)
\end{thm}
\begin{rdef}{ Remark}



Note, that as it follows from Theorem~\ref{scPet} ( \cite{petrunin-SC}),
one can always pass to a subsequence of $M_n$ to make $a_n^{hom}\#\Sc_{M_n}$ converge.
Thus, the point is that the limit does not depend on the sequence.
In particular, one can define the scalar curvature of smoothable Alexandrov space as the measure $\mu$ above and this definition does not depend on the choice of smoothing.
\end{rdef}
\begin{thm}{Corollary}\label{CorUniform}
Given $\kappa\in\RR$
and $D,v,\eps>0$,
there is $\delta=\delta(\kappa,D,v,\eps)>0$ such that
if $M$ and $M'$ be two Riemannian manifolds such that
\begin{enumerate}
\item $\sec M$, $\sec M'\ge \kappa$  ,
\item $\vol M$, $\vol M'>v$,
\item $\diam M$, $\diam M'\le D$
\item $\GHdist(M,M')<\delta$
(Here $\GHdist$ stays for Gromov--Hausdorff distance.)
\end{enumerate}
then
$$\l|\int\limits_{M}\Sc_M-\int\limits_{M'}\Sc_{M'}\r|<\eps.$$

\end{thm}

Indeed,  
the set of manifolds $M$ with
$\sec M\ge \kappa$ and  $\diam M\le D$
 is pre-compact w.r.t. Gromov--Hausdorff metric and any 
 Cauchy sequence converges without collapse to some 
 Alexandrov space, due to the lower bound on the volumes.
Then \ref{CorUniform} follows from \ref{CorSc}
because of uniform continuity  of continuous function on compactum.




\subsection{Localization. Notation for classes of convergent spaces}
Our main theorem is  a local result
and for our proof
 we need formally more strong, local version of our theorem
 (when reducing higher dimensions to 3 or 2 dimension we deal with level sets of concave
 function, which have structure of Alexandrov space only locally).
 Here we describe this local structure. We also
  introduce uniform notation for classes of Alexandrov spaces with local structure
 and complete spaces.
% We can write all our proofs for spaces with lower bound on curvature $\kappa=-1$, so we  define our classes with this curvature bounds.
 
 
 
 Let $B_r(O)\subset \R^m$ denotes a ball of radius $r$
 and center at $O$.
 
 
 
 Let 
$\rho: B_R(O)\times B_R(O)\to\R_+$ be intrinsic
locally Alexandrov metric. By locally Alexandrov we mean that  any point
has a neighborhood such that any triangle with vertexes in this neighborhood
satisfy 
Alexandrov comparison with curvature $\ge -1$.
We call this metric metric {\it an admissible Alexandrov metric.}
If in addition this
metric is locally isometric to a Riemannian
manifold  then we
call this metric
an admissible Riemannian metric.
Suppose that for some $0<r<R/3$
we have the following.
Distances between any two points in
$B_{r}(O)$
 are realized by  length of
 shortest paths in
 $B_{2r}(O)$ and 
 for all triangles with vertexes  in
$B_{r}(O)$
 Alexandrov comparison with curvature $\ge -1$
  hold. We call this metric
{\it an admissible Alexandrov metric on  $B_R(O)$ with a core $B_r(O)$.}
  If in addition this
metric is locally isometric to Riemannian
manifold with sectional curvature $\ge -1$, then we
call this metric
{\it an admissible Riemannian metric on  $B_R(O)$ with a core $B_r(O)$.}


We say that a metric space $X$
is {\it an admissible Alexandrov domain} or {\it an admissible  Riemannian domain} correspondingly
 if there exists an admissible Alexandrov  or an admissible Riemannian metric    $\rho$ on $B_R(O)$
 with a core $B_r(O)$ such  that
$X$
is isometric to
$(B_{r}(O),\rho)$.

We denote by
$\A$ the union of class of Alexandrov spaces with curvature $\ge -1$
and a class of admissible Alexandrov domains.

We denote by
$\M$ the union of
a class of Riemannian manifolds
with sectional curvature $\ge -1$
and a class of  admissible Riemannian domains.


Let $\{A_n\}_{n=1}^\infty$, $A$ be metric spaces and $a_n:A_n\to A$
homeomorphisms. We will write
{$\boldsymbol {(A_n, A,  a_n)\in\mathcal{SAA}}$} in one of the following two cases:

1) 
$A_n$ and $A$  are
admissible Alexandrov domains such that for some 
$R>r>0$ the following holds. 
Each of these spaces can be presented as  
a core $B_r(O)$ of some admissible Alexandrov metric
 on $B_R(0)$ and these admissible Alexandrov metrics
 converge. Homeomorphisms
 $a_n$ come from identification  $A_n$ and $A$ with
$B_{r}(0)$. 
   
2) $A_n$ and $A$ are Alexandrov spaces with curvature bounded below by
$-1$ and $A_n\GHto A$ via homeomorphisms
$a_n: A_n\to A$.

%Let $(M_n, A,  a_n)\in\mathcal{SAA}$ and all $M_n$ are locally isometric
%to Riemannian manifold with sectional curvature $\ge -1$. In this case we write
%$(M_n, A,  a_n)\in\mathcal{SMA}$

Let $\{M_n\}_{n=1}^\infty$, $A$ be metric spaces and $a_n:M_n\to A$
homeomorphisms. We will write
$\boldsymbol {(M_n, A,  a_n)\in\mathcal{SMA}}$ in one of the following two cases:

1) 
$M_n$ are admissible Riemannian domain and $A$  is
admissible Alexandrov domain such that for some 
$R>r>0$ the following holds. 
Each of $M_n$ can be presented as  
a core $B_r(O)$ of some admissible Riemannian metric
 on $B_R(0)$
and $A$ as
a core $B_r(O)$ of some admissible Alexandrov metric
 on $B_R(0)$ and these admissible Riemannian metrics
 converge to this admissible Alexandrov metric. Homeomorphisms
 $a_n$ come from identification  $A_n$ and $A$ with
$B_{r}(0)$. 
   
   2) $M_n$
are complete Riemannian manifolds with sectional curvature $\ge -1$,
 $A$ is Alexandrov spaces with curvature bounded below by
$-1$ and $M_n\GHto A$ via homeomorphisms
$a_n: M_n\to A$.
   


\subsection{ Background }
{\bf Analysis on Alexandrov spaces}

Our proof relies on
Perelman theory of
  $DC$ functions on Alexandrov spaces (\cite{PerDC}).
 There is a $DC$ chart in a neighborhood 
 of any regular point in Alexandrov space,
metric tensor 
is of bounded variation
in this  chart and
Cristophel symbols are signed Radon measure.
We modify this theory slightly to adjust
it for sequences of spaces. (section~\ref{sec:DC}, section~\ref{sec:metr-con}).
 

{\bf Curvature and measure}

It is known that curvature of $2$-dimensional Alexandrov space
is a signed Radon measure and for any smoothing
by Riemanian manifolds
the intrinsic curvature of the sequence 
weakly converges to this measure (see for example Reshetnyak).
This is exactly the statement of our
 Main theorem in dimension $2$.
 Our proof of the Main theorem for higher dimensions is based on  
this statement.

The second important thing we use is 
the uniform boundness of curvature  for manifolds provided by
the following Petrunin's theorem (\cite{petrunin-SC}) and
the corollary. This implies
that any sequence of "curvature measures" contains 
a weakly converging subsequence, so
to prove a weak convergence of such a sequence
it is sufficient to prove that any two partial limits coinside.

\begin{thm}{Theorem}\label{scPet}
Let $M$ be a complete Riemannian m-manifold with sectional
curvature $ \ge -1$. Then for any $p \in M$, $r<1$
$$\int_{B_r(p)} \Sc\le Const(m)r^{m-2},$$
where $B_r(p)$ denotes the ball of radius $r$ centered at $p\in M$ and $\Sc$ is a scalar curvature
of M.
\end{thm}

\begin{thm}{Remark}\label{rem:scPet}
The theorem remains true if we replace a complete Riemannian 
manifold by local Riemanian manifold $M$ and $r<\min\{diam M, 1\}$.
The proof in
\cite{petrunin-SC}
works also for this case.

\end{thm}

The straightforward consequence is the following:

\begin{thm}{Corollary}\label{Kbound}
Let $M$ be a complete Riemannian m-manifold with sectional
curvature $K_{\sigma} \ge -1$ or
local Riemanian manifold  and $r<\min\{diam M, 1\}$.
We denote $K_{max}(x)=\sup_{\sigma\subset T_xM} |K_\sigma|$
for any point $x\in M$. Then for any $p\in M$,

$$\int_{B_r(p)} K_{max}\le Const(m)r^{m-2}.$$


\end{thm}


\section{Functions, tensors and convergence for Alexandrov spaces}

\medskip
In this section we give definitions necessary for the formulation 
of the main theorem.

%Everywhere in this section $M_n, A, a_n)$

%$A_n\GHto A$ is a converging sequence of Alexandrov spaces
%with a fixed approximation sequence $a_n:A_n\to A$. 


%Let $A$ be a finite dimensional Alexandrov space with curvature bounded below.
 
\subsection{Continuous functions and the dual space of measures}

Let us denote by $C(A)$  the space of continuous functions on $A$
with a compact support and supplied by a uniform norm.
We denote by $C^*(A)$ 
the space of continuous linear functionals on $C(A)$   with weak topology.
It is known that this space coincide with a
space of signed Radon measures.
We call elements of $C^*(A)$ just \emph{measures}.
We  denote by $<h|f>$ the value of $h\in C^*(A)$ on $f\in C(A)$.
\emph{Weak convergence} of measures $m_n\in C^*(A)$ 
to $m\in C^*(A)$ (we denote it $m_n  \rightharpoonup m$) means that for
any
$f\in C(A)$ the sequence $<m_n|f>\to <m|f>$.

For a given
$(A_n, A, a_n)\in \SAA$ 
 %approximation  sequence $a_n:A_n\to A$
 we define convergence of functions
 and measures as follows.
We say that  a sequence $f_n\in C(A_n)$
uniformly converges to $f\in C(A)$ and write
$f_n\stackrel{C}{\rightarrow}f$
if $| f_n   \circ a_n^{-1}-f|\to 0$.
We say that  a sequence
of measures 
$m_n\in C^*(A_n)$ weakly
converges to $m\in C^*(A)$
$\rightharpoonup$
if for pushforward measures $m_n\circ a_n^{-1}\rightharpoonup m$.




%We will denote by $<h|f>$ the value of $h\in C^*(A)$ on $f\in C(A)$.

\subsection{ Smooth structure}
Let $A\in \A$
and $(M_n, A, a_n)\in\SMA$.


Let us fix small $r>0$
$p\in A$
and define smoothed distance function as $$d=\widetilde{dist}_{B_r(p)} =\oint_{B_r(p)} \dist_{x}dx.$$ 
 
 We can define lifting of this function if fix
  some lifting sequence of points $M_n\ni p_n\to p\in A$ by the same formula:
$$d_n=\widetilde{dist}_{B_r(p_n)}$$

Now we define vector fields convergent as good as gradients of smoothed distance
functions. We say that a sequence of vector fields
$v_n$ on $M_n$ \emph{converges} if for
every point  $x \in A$, any smoothed distance function
$ d= \widetilde{dist}_{B_r(p_n)}$ and its liftings
$d_n = \widetilde{dist}_{B_r(p_n)}$ there is a neighborhood $U \ni x$ and a
 constant $c > 0$, so that for
every sequence of points $M_n\ni  y_n\to y\in U$
$$\limsup_{n\to\infty} <\nabla d_n,v_n>(y_n)-
 \liminf_{n\to\infty} <\nabla d_n,v_n>(y_n)\le$$
 $$c(\limsup_{n\to\infty} |\nabla d_n|(y_n)-
 \liminf_{n\to\infty} |\nabla d_n|(y_n)).
 $$
 
 
 We say that a sequence of 
 $C^1$ functions $f_n:M_n\to\R$
 $C^1$-converges in Alexandrov sence % to $f:A\to\R$
 and write $f_n\ccto f$
 if $f_n\cto f$ and
  the sequence $\nabla f_n$ converges.
 
 
 
  We say that a function $f:A\to\R$
 is Alexandrov smooth
( $f\in C^1_{Aex}$)
 if there sequence of smooth functions $f_n:M_n\to\R$
such that
 $f_n\ccto f$.
 
 In \ref{} we prove that smoothed distance functions itself are
 Alexandrov smooth.
 
 \begin{thm}{Remark}
 It is possible to define a notion of a smooth function
 also for nonsmoothable Alexandrov space, 
 but it would be technically comlicated while we don't formally need this.
 It also can be proved that definition doesn't depend on smoothing
 sequence, we also skip this.
 In addition all examples of smooth functions we know comes as
 compositions of smoothed distance function.
  
 \end{thm}
 
\subsection{Tensors}


\begin{rdef} {Definition}\label{def:mestens}
Let $A\in \A$.
A \emph{vector measure } $\mathfrak{v}$  on $A$
is a continuous linear map
$\mathfrak{v}\:C^1_{Aex}(A)\to C^*(A)$ which satisfies
chain rule;
i.e. for any collection  $f_1,f_2,\dots,f_\kay \in C^1_{Aex}$
and a smooth function $\phi\:\RR^\kay\to\RR$ we have
$$\mathfrak{v}(\phi(f_1,f_2,\dots,f_n))
=
\sum_{i=1}^n (\partial_i\phi)(f_1,f_2,\dots,f_n)\cdot\mathfrak{v}(f_i)$$
where $\partial_i$ denotes partial derivatives in $\RR^n$.

Analogousely, we define (contravariant) measure tensor field.
A \emph{measure tensor } $\mathfrak{t}$ of valence $\kay$ on $A$ is a multilinear map of $\kay$ variables in $C^1_{Aex}(A)$ with values in $C^*( A)$ which satisfies chain rule in each of the arguments.


\end{rdef}









\begin{rdef} {Definition}
Assume $\mathfrak{t}_n$ is a sequence of uniformly 
bounded  measure tensors on $M_n$  and $\mathfrak{t}$ is a
measure tensor on $A$,
all of the same valence $\kay$.
We say that $\mathfrak{t}_n$ weakly conveges to  $\mathfrak{t}$
(briefly $\mathfrak{t}_n\rightharpoonup\mathfrak{t}$) if for arbitrary $\kay$
sequences that
$C^1$-converge in Alexandrov sence
$f_{i,n}\to f_i, i=1,\dots,\kay$, the measures $\mathfrak{t}_n(f_{1,n},f_{2,n},\dots,f_{\kay,n})$ weakly converge to $\mathfrak{t}(f_{1},f_{2},\dots,f_{\kay})$.
\end{rdef}

% \begin{thm}{Corollary}\label{limitTensor}

\section {Curvature measure tensor and Main theorem}

The curvature of a smoothable $m$-dimensional Alexandrov space $A$
will be described using a tensor distribution $\mathfrak{q}=\mathfrak{q}_A$ of valence $2\cdot(m-2)$.
Our Main theorem claims the weak convergence
of this tensors if we have a smoothing $M_n\GHto A$.
Let us start with a two dimensional case, 
in this case the statement of the Main theorem is a well known fact and
we use it as a base of our proof. 

 \subsection{Two dimensional case}

In particular case, if $m=2$ the valence of $\mathfrak{q}$ is $0$;
in this case $\mathfrak{q}$ coinsides
 with the curvature measure --- the stadard way to describe curvature of surfaces, 
(see, for example \cite{Resh}).
For a smooth surface a density of this curvature measure w.r.t. the area measure
is   a Gauss (intrinsic) curvature.
The statement of our Main theorem in this case, i.e. 
continuity of these measures under Gromov-Hausdorf convergence
is also well known.   


\subsection{Higher dimensional case}
\parbf{Curvature measure.}

For an $m$-dimensional Riemannian manifold $M$
its curvature % $\mathfrak{q}_M$
 is a smooth tensor field.
It can be described using the field of curvature operator
 $\Rm_M\:(\bigwedge^2\T)M\to (\bigwedge^2\T)M$.

We define curvature measure tensor
$\mathfrak{q}_M$ (in the sence of Definition~\ref{def:mestens}) as follows.
 For smooth functions
 $f_i,g_i:M\to\R, i=1,\dots, m-2$
with compact supports (i.e. test functions)
 we define $\mathfrak{q}_M(f_1,f_2,\dots,f_{m-2},g_1,g_2,\dots,g_{m-2})$
to be  the measure with a density
 ${q}_M(\nabla f_1,\nabla f_2,\dots,\nabla f_{m-2},\nabla g_1,\nabla g_2,\dots,\nabla g_{m-2}): M\to\R$
w.r.t. $d Vol$, which is given by:
\begin{multline*}
{q}_M(\nabla f_1,\nabla f_2,\dots,\nabla f_{m-2},\nabla g_1,\nabla g_2,\dots,\nabla g_{m-2})
=
\\
= d Vol (
\Rm_M(*(\nabla f_1\wedge \nabla f_2\wedge\dots\wedge \nabla f_{m-2}))\wedge\nabla g_1\wedge \nabla g_2\wedge\dots\wedge \nabla g_{m-2}),
\end{multline*}
where ${*}\:(\bigwedge^{m-2}\T)M\to(\bigwedge^2\T)M$ is the  Hodge star operator.

\begin{rdef}{Remark}\label{K=q}
Let note that in the case if $f_i=g_i$, for $i=1,\dots,m-2$
we have:
% can express $q_M$ using co-sectional curvature: 
$$q_M(\nabla f_1,\nabla f_2,\dots,f_{m-2},\nabla f_1,\nabla f_2,\dots,\nabla f_{m-2})=K^M(\nabla f_1,\dots,\nabla f_{m-2}).$$


Hence
sectional curvatures of $M$ can  be computed using the tensor
$\mathfrak{q}_M$.
Also the density $q_M$ is defined by the sectional curavature,
because of the symmetry:
$${q}_M(\nabla f_1,\dots,\nabla f_{m-2},\nabla g_1,\dots,\nabla g_{m-2})=
{q}_M(\nabla g_1,\dots,\nabla g_{m-2},\dots,\nabla f_1,\dots,\nabla f_{m-2}).$$
Therefore measure tensor $\mathfrak{q}_M$
gives an equivalent description of curvature of Riemannian manifold.
\end{rdef}
Now we can formulate our main result:
  
\begin{thm}{Main theorem}\label{main}
Let  $A$  be a smoothable Alexandrov space with approximations
$M_n\smooths{a_n} A$ then $\mathfrak{q}_{M_n}\rightharpoonup \mathfrak{q}_A$ 
for some measure tensor $\mathfrak{q}_A$ on $A$.
\end{thm}

\begin{thm}{Main theorem (local)}\label{mainloc}
Let  $(M_n, A, {a_n})\in\SMA$, then $\mathfrak{q}_{M_n}\rightharpoonup \mathfrak{q}_A$ 
for some measure tensor $\mathfrak{q}_A$ on $A$.
\end{thm}


\subsection{Definition of curvature tensor for a smoothable Alexandrov space  }
Main theorem~\ref{main} imply that
 curvature measure tensor can be
correctly defined for
any smoothable Alexandrov space
as a weak limit of cuvature tensors of any smoothing sequence.

\section{Plan of the proof}

     
\subsection{Proof}
 
Let $(M_n, A, a_n)\in \SMA$.


Because of the symmetry 
$${q}_M(f_1,f_2,\dots,f_{m-2},g_1,g_2,\dots,g_{m-2})=
{q}_M(g_1,g_2,\dots,g_{m-2},\dots,f_1,f_2,\dots,f_{m-2})$$  
it is sufficient
to  prove of the weak convergence 
of measures 
$$\mathfrak{q}_{M_n}(f_{1,n},\dots,f_{m-2,n},f_{1,n},\dots,f_{m-2,n})$$
with densities
$$r_n
=
{q}_{M_n}(f_{1,n},\dots,f_{m-2,n},f_{1,n},\dots,f_{m-2,n})
\:M_n\to\RR$$
for any collection of $m-2$ smooth sequences
$f_{i,n}\:M_n\to\RR$,  $i\in\{1,2,\dots,m-2\}$,
such that
$f_{i,n}\ccto f_i   $.

Recall that
$${q}_{M_n}(f_{1,n},\dots,f_{m-2,n},f_{1,n},\dots,f_{m-2,n})(x)=
|\nabla f_{1,n}(x)\wedge\dots \wedge\nabla f_{m-2,n}(x)|^2\cdot K_\sigma, $$
where $K_\sigma $ is the sectional curvature at $x\in M_n$
on a plane orthogonal to 
$\nabla f_{1,n}(x)\wedge\dots \wedge\nabla f_{m-2,n}(x)$.
Since gradients are bounded the
Corollary~\ref{Kbound} of Petrunin's theorem (\cite{petrunin-SC})
implies that
 for any point $p\in M_n$ and $r<1$,
$$\int\limits_{B_r(p)}|r_n|\le \Const\cdot r^{m-2}.\eqlbl{sc-pet}$$
 
This boundness of measures
is the crucial point for our proof.
Firstly this makes possible
 passing to a subsequence of $M_n$ such that
measures with densities $r_n$  converges.
So, we verify 
 that if $\mathfrak{r}_1$ and $\mathfrak{r}_2$ are two such partial limits 
for different subsequences then $\mathfrak{r}_1=\mathfrak{r}_2$.
To do this
we partition $A$ into three subsets $A^\circ$, $A'$ and $A''$ and separately prove that $\mathfrak{r}_1$ and $\mathfrak{r}_2$ coincide on each of these subsets (claims~\ref{A''}, \ref{A'} and \ref{A^0}).
The partition is constructed as follows
\begin{enumerate}
\item $A^\circ=\set{x\in A}{\T_x\ \text{is isometric to}\  \RR^m}$ --- the set of regular points.
\item $A'=\set{x\in A\backslash A^{\circ}}{\T_x\ \text{is isometric to}\  \RR^{m-2}\times \Cone^2}$ the set of singular points of codimension two.
\item $A''$ --- the rest, i.e. $A''=A\backslash (A^{\circ}\cup A')$ the set of singular points of codimension three and larger.
\end{enumerate}


 Proofs for $A'$ and $A''$ (for exact formulation see \ref{A''}, \ref{A'} and for proofs \ref{sec:cone},
 \ref{sec:blow}, \ref{sec:codim2}, \ref{sec:codim3})
 are self-contained and don't differ for local and global theorems and for different dimensions.
  For the set  $A^\circ$  we use a sort of induction which includes local version of Main
  theorem (for plan see \ref{sec:A0} and proof \ref{sec:regular}).
  
  Passing to partial limits
 $\mathfrak{r}_1$, $\mathfrak{r}_2$
is convenient for formulations, but in the prove we don't pass to
convergent subsequences, but verify weak convergence of
measures in the sense of definition \ref{deltaconv1}.
While there is still
the point in the proof where we strongly rely on uniform boundness 
of measures: we prove convergence of integrals 
not for all continuos functions as a test functions, but
only for
smooth functions (this works because of Lemma~\ref{smoothmeasure}).   




\subsection{The set $A''$ of  singularities of higher codimension }
According to \cite[???]{BGP}, the $(m-2)$-hausdorff measure of $A''$ vanishes.
Thus, from \ref{sc-pet}, we get

\begin{thm}{Claim}\label{A''}
$\mathfrak{r}_1|_{A''}\equiv\mathfrak{r}_2|_{A''}\equiv0$.
\end{thm}

\subsection{The set $A'$ of codimension 2 singularities  }
Consider function $\omega\:A\to\RR$ defined as
$$\omega(p)=2\cdot\pi\cdot\l(1-\frac{\vol\Sigma_p}{\vol\SS^{m-1}}\r).$$
Clearly $\omega|_{A^\circ}\equiv0$, further according to \cite[??? and ???]{BGP}, the
functioin $\omega\:A\to\RR$ is ???-semicontinuous.
If $p\in A'$, i.e. $\T_p=\RR^{m-2}\times \Cone^2_p$, then the total angle of $\Cone^2_x$ is equla to $2\pi-\omega(x)$.

Given an array of Alexandrov smooth
sequences $\bm{f}=(f_1,f_2,\dots,f_{m-2})$, and $x\in A''$
one can consider the restriction of differential $\d_x\bm{f}=(\d_xf_1,\d_xf_2,\dots,\d_xf_{m-2})\:\T_x\to \RR^{m-2}$ to $\RR^{m-2}\times 0\in \RR^m\times\Cone^2_x=\T_x$.
If this restriction is linear, define $\theta_x(f_1,f_2,\dots,f_{m-2})$ the square of its determinant.

Further, let us denote by $h_\alpha$ the $\alpha$-dimensional Hausdorff measure.

\begin{thm}{Claim}\label{A'}
Measures
$\mathfrak{r}_1$ and
$\mathfrak{r}_2$ are
 absolutely continuous with respect to
 $h_{m-2}$ (this follows from \ref{sc-pet}). 
 Moreover,
 if we take restriction on $A'$ for measures
 the density for both
 $\mathfrak{r}_1$ and
$\mathfrak{r}_2$ will be the same, namely 
$ \omega(x)\cdot\theta_x(f_1,f_2,\dots,f_{m-2})$
 for any point $x\in A'$, i.e. for any subset $X\subset A'$
 
 $$\int_Xd\mathfrak{r}_1=\int_Xd\mathfrak{r}_2=\int_X
\omega(x)\cdot\theta_x(f_1,f_2,\dots,f_{m-2}) d h_{m-2} $$
 
  
 %$\mathfrak{r}_1|_{A'}=\mathfrak{r}_2|_{A'}=\omega(x)\cdot\theta_x(f_1,f_2,\dots,f_{m-2})\cdot h_{m-2}|_{A'}$.
\end{thm}

We first prove this claim in the partial case, $A=\Cone\times\RR^{m-2}$
(section \ref{sec:cone}); then extend it by rescaling and passage to the limit (section \ref{sec:blow}).

\subsection{The set $A^\circ$  of regular points }\label{sec:A0}
This is the most difficult case.

We recall that
$$A^{\circ}=\bigcap_{\delta>0} A^\delta,$$
where $A^\delta$ denotes the set of $\delta$-strained points of $A$.
Then to show that
$\mathfrak{r}_1|_{A^o}\equiv\mathfrak{r}_2|_{A^o}$
it is enough to show the following

\begin{thm}{Lemma}\label{A^0}
Let $\nu=|\mathfrak{r}_1-\mathfrak{r}_2|$.
Then for any $x\in A^\circ$, there is a neighbourhood $U_x\ni x$ such that
$$\nu({A^\delta\cap U_x})\le \Const\cdot\delta$$
for some fixed $\Const\in\RR$, independent of $\delta$.
\end{thm}
 
The proof uses reduction to lower dimensions as follows.
 We use Main theorem (local) for dimension 2 (which is well known) as a base step.
 Then we proof  Lemma~\ref{A^0} for dimension 3.
 Then we obtain Main theorem (local) for dimension 3.
 Then we reduce general case of Lemma~\ref{A^0} to 
   the Local theorem for dimension 3. 
    
 
Let note that the lemma asserts 
weak $ c\delta$-convergence 
of measures with densities $r_n$ on $A^\delta\cap U_x$ in the sense
of definition~\ref{deltaconv2},  but  in the proof
we don't pass to patial limits and
verify convergence for smooth function as a test function
(Lemma~\ref{smoothmeasure}).
 
 

  Now we sketch the proof of this lemma in dimension 3. 
  For a given smooth sequence $f_n\to f$
  we need to prove 
  weak  $c\delta$-convergence
of
$q_n(\nabla f_n, \nabla f_n)dVol_n$ 
 on ${A^\delta\cap U_x}$. 
 
 For Riemannian manifold $M$
we  introduce a quadratic
form Strange curvature:  $Str(w,w)=\Sc\cdot |w|^2-Ric(w,w)$,
which in dimension 3 completely defines curvature tensor.
Namely, for 6 vectors $v_i$ in general position we have:
$$q(w, w)=\sum _{i=1}^{6}\alpha_i(w,w)\Str(v_i,v_i),\eqlbl{R=Str}$$
where $\alpha_i(w,w)$ depends on scalar products.
In such a way we reduce the proof of weak  $c\delta$-convergence
of
$q_n(\nabla f_n, \nabla f_n)dVol_n$
to the proof of weak $c\delta$-convergence of 
$\Str(\nabla g^i_n, \nabla g^i_n)dVol_n$ 
on
${A^\delta\cap U_x}$
curvature for 6 converging sequences $g^i_n\ccto g$
with gradients $\nabla g^i$ in general position near $p$ .
 
 
 So our main technical ingredient is convergence of Strange curvature,
 let us describe this in more details.
 
 We are deal with a special type of $C^1_{Alex}$-converging sequences 
  - Nice sequences which are defined locally (see Definition~\ref{def:Nice} ).
  
  \begin{thm}{Lemma}\label{Str(v,v)}
  For any $p\in A^0$ and $v\in T_pA$
  there is a neighborhood $V_p$ and a Nice sequence 
  $g_n:a_n^{-1}(V_p)\to\R$, $g:V_p\to\R$,
    $g_n\ccto g$,
   such that measures $\Str(\nabla g_n, \nabla g_n)dVol_n$
  weakly $c\delta$-converges on
  ${A^\delta\cap V_p}$  and $d_pf$
  is arbitrary close to $-\<v,\cdot\>$.
  
  \end{thm}
  
  
 For the proof of this lemma we use 
 expression for Strange curvature for Riemannian 
 manifold,
namely
 a Bochner-type formula \ref{Bochner}
(section~\ref{sec:Bochner}).

To prove convergence of
integrals in this
 formula (section \ref{sec:str}) we use
special chart with common domain for all the sequence and the limit space
 around a  point $p\in A^0$
-
a
Nice common chart (see definition in section\ref{sec:Nice}).
This are
homeomorphism
$\mathfrak X:U\to\Omega\subset\R^3$
and diffeomorphisms
$\mathfrak X_n:U_n\to\Omega\subset\R^3$.
This common chart is a generalization of Perelman $DC$-chart 
(\cite{PerDC}) for a given Alexandrov space to the case
of a given smoothing sequence converging to Alexandrov space.
This makes possible to apply 
the technique of
$DC$ (difference concave) functions in $\R^3$ (sections~\ref{sec:DC}, \ref{sec:metr-con}).
Here we rely on
 ( generalized for the case of  sequences)
 results from
\cite{PerDC}, which assert that
a  components of
metric tensor are $BV$ (bounded variation) in the charts and Cristoffel simbols
are signed Radon measures.


The  other thing we use here
is the convergence of 
Gauss curvature in
$2$-dimensional case
($2$-dimensional smoothable Alexandrov
spaces arise as level sets of concave functions.) 

Let note also that error $c\delta$ on $A^\delta$
 arises only because
of $c\delta$-convergence of  norms of  gradients of $C^1_{Alex}$-convergent sequences,
these norms
appear  when we express $3$-volume  via $2$-volume of level sets.



 
The proof of Lemma~\ref{A^0} for higher dimensions
relies on the Main theorem (local version) for dimension 3.

\section{Tools}
\subsection{Bochner formula}
\label{sec:Bochner}
Here we rewrite Bochner formula, in such a way that each term has geometric meaning.
Let $M$ be Riemannian $m$-manifold and $f\:M\to\R$ be a smooth function without critical points on an open domain $\Omega\i M$.
Assume $\phi\:\Omega\to\R$ be a smooth function with compact support.
Set $u=\nabla f/|\nabla f|$.
Let us define $\Int_f(x)$ (or just $Int$) to be scalar curvature of the level set $L_x=f^{-1}(f(x))$ at $x\in L_x\i M$.
Set
\begin{enumerate}
 \item $\kappa_1(x)\le\kappa_2(x)\le\dots\le\kappa_{m-1}(x)$ the principle curvatures of $L_x$ at $x$;
 \item $H=H(x)=\kappa_1+\kappa_2+\dots+\kappa_{m-1}$ is mean curvature of $L_x$ at $x$
\item $G=G(x)=2\sum_{i<j}\kappa_i\cdot\kappa_j$ is the extrinsic term
 in the Gauss formula for $\Int_f(x)$.
\end{enumerate}
Then the following formula of Bochner type holds:
$$\int\limits_\Omega \phi\cdot \Str(u)
=
\int\limits_\Omega \l[H\cdot\<u,\nabla\phi\>- \<\nabla\phi,\nabla_u u\> \r]+
\int\limits_\Omega \phi\cdot \Int(u)\eqlbl{Bochner}$$
This identity will be refered further as \emph{Bochner formula}.
%$$\int\limits_\Omega \phi\cdot (G-\Ric(u,u))=
%\int\limits_\Omega \l[H\cdot\<u,\nabla\phi\>- \<\nabla\phi,\nabla_u u\> \r] $$

\parit{Proof.}
Let us write Bochner formula for field
$u$:  {\bf ref??}
$$D^2u-\nabla^*\nabla u=\Ric(u)$$
Now let us integrate
\begin{align*}
\int\limits_\Omega\phi\cdot\l[\<D u,D u\>-\<D^2 u, u\>\r]
&=
\int\limits_\Omega\<\nabla\phi{.}u,D u\>
=
\\
&=
-\int\limits_\Omega\l[H\cdot\<\nabla\phi,u\>- \<\nabla\phi,\nabla_u u\> \r],
\end{align*}
here ``${.}$'' denotes Kliford multipliccation.
Since $| u|\equiv 1$, we have $\<\nabla_{\nabla\phi}  u, u\>=0$.
Therefore
$$\int\limits_\Omega\phi\cdot\l[\<\nabla u,\nabla u\>-\<\nabla^*\nabla u, u\>\r]
=
\int\limits_\Omega\<\nabla_{\nabla\phi}  u, u\>=0,$$
where $\<\nabla u,\nabla u\>=\sum_i\<\nabla_{b_i} u,\nabla_{b_i} u\>$ for an orthonormal basis $\{b_i\}$ ---
clearly, this expression does not depend on choice of $\{b_i\}$.

Therefore
\begin{align*}
\int\limits_\Omega 2\cdot\phi \cdot G
&=\int\limits_\Omega\phi\cdot(\<D u,D u\>-\<\nabla u,\nabla u\>)
=
\\
&=
\int\limits_\Omega \phi\cdot \Ric(u,u) -\int H\cdot\l[\<u,\nabla\phi\>- \<\nabla\phi,\nabla_u u\> \r].
\end{align*}

% {\bf ? coefficient 2 ?}

Then applying Gauss identity $\Int=G+(\Sc-2\Ric(u,u)$
we obtain
\ref{Bochner}.

\subsection{ Auxiliary spaces  and functions}


\subsubsection{Nice functions}\label{sec:Nice}
\begin{thm}{Definition}\label{def:Nice}

Let $(M_n, A, a_n)\in \mathcal{SA}$,
$V\subset A$ be an open set
and $V_n=(a_n)^{-1}(V)$.
We say that a sequence
of smooth functions
$f_n:V\to\R$ 
converging $f_n\ccto f:V\to\R$
is
\emph{ a Nice sequence}
if all
 $f_n$ are uniformly strictly concave . 

\end{thm}


\begin{thm}{Definition}
Let $A\in \A$ and $U\subset A$ be an open set.
Let
$ f^1, \dots , f^k:U\to\R$ be a  collection
 of semiconcave functions.
 The map
 $F=(f^1, \dots , f^k):U\to\R^k$ is called \emph{$\varepsilon$-tight} 
 if
$$\sup_{x \in, i\neq j}\{ d_xf_i(\nabla_xf_j)\}<-\varepsilon.$$
\end{thm}

\begin{thm}{Definition}
Let $(M_n, A, a_n)\in \mathcal{SA}$,
$V\subset A$ be an open set
and $V_n=(a_n)^{-1}(V)$.
A sequence of tight maps
$F_n=(f_n^1,\dots,f_n^m):V_n\to\R^m$
is
\emph{a Nice sequence of tight maps}
converging to
$F=(f^1,\dots,f^m)$
if the following two conditions hold:

1)
$f_n^i \to f^i$,
is
a
 Nice sequence
 for all $i\in\{1,\dots, m\}$

2) there exists  a
Nice sequence 
$f_n^0\to f^0$ and $\varepsilon_0>0$
such that
$f^0, f^1,\dots,f^m$ is
$\varepsilon_0$-tight collection and 
$f_n^0, f_n^1,\dots,f_n^m$ are
$\varepsilon_0$-tight collections for all $n$. 

\end{thm}


\begin{thm}{ Proposition}
Let $(M_n, A, a_n)\in \mathcal{SA}$,
$V\subset A$ be an open  set
and $V_n=(a_n)^{-1}(V)$.
Let $F_n=(f_n^1,\dots,f_n^m):V_n\to\R^m$
be a Nice   sequence  of tight maps
converging
to $F=(f^1,\dots,f^m)$.
Then for any $p\in V$ there is an open neighborhood $V^p\subset V $
such that
$F|_{V^p}$ is a bi-Lipschitz  homeomorhism onto the image,
all  $F_n|_{(a_n)^{-1}(V^p)}$ are diffeomorhisms with uniform on $n$ bi-Lipschitz 
constant.

\end{thm}

For the proof see \cite{petrunin-SC}.

It follows that in notation of proposition for any open $\Omega$ such that $\overline\Omega\subset F(V_p)$
we have ${F_n((a_n)^{-1}(V^p))}\supset \Omega $ for large $n$
and the sequence of homeomorhisms
$$\widetilde{a_n}=F_n\circ F^{-1}|_{F_n^{-1}(\Omega)}:F_n^{-1}(\Omega)\to F^{-1}(\Omega)$$
is an approximation of 
$F^{-1}(\Omega)$
equivalent to the initial approximation $a_n$.

In this case we call a sequence of
diffeomorphisms $F_n|_{F_n^{-1}(\Omega)}\to\Omega$
together with a homeomorphism $F|_{F^{-1}(\Omega)}\to\Omega$
\emph{a Nice common chart sequence}.

 Further we 
 use the following notation for domain and functions in
 Nice common chart sequences 
 
$$ \mathfrak X=(\mathfrak x^1,\dots,\mathfrak x^m): U\to\Omega,$$
$$\mathfrak X_n=(\mathfrak x^1_n,\dots,\mathfrak x_n^m):U_n\to\Omega,$$

   (i.e.  $U=F^{-1}(\Omega), U_n=F_n^{-1}(\Omega),
 \mathfrak X=F|_{F^{-1}(\Omega)}, \mathfrak X_n=F_n|_{F_n^{-1}(\Omega)}$).


\subsubsection{Existence of Nice sequences and Nice common chart sequences }

  
 \begin{thm}{Lemma}
 Let $(M_n, A, a_n)\in \SMA $.
 For any
 $p\in A$, $v\in T_pA$,
 $\varepsilon>0$
 there is a neighborhood $U\ni p$
 and a
 Nice sequence
 $f_n: a_n^{-1}(U)\to \R$
 $f_n\ccto f$
such that $d_pf$  is arbitrary close to $ <v,\cdot>$.
 \end{thm}
 
 The proof will be in Appendix.
 

\begin{thm}{Lemma}\label{existenseTight}
Let $(M_n, A, a_n)\in \SMA $.
 Let
 $p\in A$ and $v_0, v_1,\dots,v_m\in T_pA$
 be such that $\angle(v_i, v_j)>\pi/2+\varepsilon$ for $i\neq j$ and some
 $\varepsilon>0$. Then
 there exists
 a Nice common chart sequence
$F_n=(f_n^1,\dots,f_n^m):U_n\to\R^m$
with a limit chart
 $F=(f^1,\dots,f^m):U\to\R^m$,
 such that 
 $U\ni p$
and differentials $d_p f^i$ for $i=1, 2,\dots, m$
 can be made arbitrary close to $-\<v_i,\cdot\>$.
 
 
 \end{thm}
 
 
 The proof will be in Appendix.
 
 \subsubsection{     Main property of a NICE common chart.                          }\label{Cc}




We use
Nice coordinate chart sequence when
we prove convergence of Strange curvature
in a neighborhood of a regular point (section~\ref{sec:str}) .
The only thing that we use formally after 
passing to coordinate expression is the following fact about 
metric tensors in coordinate.
Components of metric tensors $g_{ij}^n$
in common Nice coordinates
are of uniformly bounded variation ($BV$) and converges  point-wise
to
limit component of metric tensor $g_{ij}$  outside
image of singularity  set (see Appendix, Theorem~\ref{metricBV}). 
This is a modification for a smoothing sequence of the G. Perelman
result, that components of metric tensor of Alexandrov space are of bounded
variation in $DC$-chart (see \cite{PerDC}).
Our computation in charts rely only on this fact  and a theory of
$BV$-functions in $\R^n$ (see Appendix) .

 
\section{Proof of Lemma~\ref{A^0} for dimension 3}\label{sec:regular}
\subsection{Convergence of Strange curvature for dimension 3}\label{sec:str}

In this section we prove
Lemma~\ref{Str(v,v)}
the main technical ingredient for
Lemmma~ \ref{A^0} in the three dimensional case.
%As it was mentioned, for $3$-dimensional case Strange curvature tensor defines curvature tensor (\ref{R=Str}). 

In the next lemma we prove weak
$\delta$-convergence on $A^\de$
 of Strange curvature 
for one of the coordinate
sequences   in 
a Nice common chart collection.
For any vector $v\in TpA$
we can complete it to  a  collection of $4$ vectors in $T_pA$
with strictly obtuse angles between each other and
 than apply Lemma~\ref{existenseTight} to obtain a Nice common chart
collection, such that in the limit chart
$\mathfrak X=(\mathfrak x^1,\mathfrak x^2,\mathfrak x^3):V_n\to\Omega$
the differential
$d_p\mathfrak x_1$ is arbitrary close to $-\<v,\cdot\>$.
Let also note that in view of
Corollary~\ref{Kbound}
Lemma~\ref{smoothmeasure}
could be applied for measures $\Str(u_n, u_n)dVol_n$ and hence
Lemma~\ref{Str(v,v)} can be reduced to
the 
 Lemma~\ref{lemma:maincoord} below.
 
 Let note that instead of  normalized gradients of coordinate functions  we 
could take normalized gradients of arbitrary Nice sequence, the proof would be almost 
the same. We take coordinate function only for convenience to have 
natural common $2$-coordinates on level sets that we need in the proof of
\ref{Int-alm-conv}.

\begin{thm}{Srange curvature lemma} \label{lemma:maincoord}
Let
$$\mathfrak X_n=(\mathfrak x_n^1,\mathfrak x_n^2,\mathfrak x_n^3):V_n\to\Omega,\qquad
\mathfrak X=(\mathfrak x^1,\mathfrak x^2,\mathfrak x^3):V\to\Omega$$
be a Nice common chart
collection around $p\in V$,
 we denote by $u_n=\nabla  \mathfrak x_n^1/|\nabla\mathfrak x_n^1|$.

Then there are open set $\Omega^*\ni \mathfrak X(p)$ and $c>0$
such that
for any
smooth function $\phi\:\Omega\to\R$
 with compact support
$\supp \varphi \subset \Omega^*\cap\mathfrak X (A^\delta)$ and $|\varphi|\le 1$
 the following holds 
 for the lifting
 $\psi_n=\mathfrak X_n\circ \varphi_n$: 
$$\limsup_{n\to\infty} \int\limits_{V_n}\Str_n(u_n)\psi_ndVol_n-
\liminf_{n\to\infty} \int\limits_{V_n}\Str_n(u_n)\psi_ndVol_n<c \delta.$$


\end{thm}
We want to apply Bochner formula \ref{Bochner}
to the functions $\mathfrak x^1_n$.
So we denote by
   $\Int_n=\Int_n(x)$ (correspondently $H_n=H_n(x)$)   an intrinsic curvature
 (correspondently mean curvature) of the level set
$(\mathfrak x^1_n)^{-1}(\mathfrak x^1_n(x))$ at $x\in  V_n$.
Applying Bochner formula,
we can reduce the proof of the 
Lemma~\ref{lemma:maincoord} to the following two lemmas:

\begin{thm}{Lemma}\label{H-converges}
Let
$$\mathfrak X_n=(\mathfrak x_n^1,\mathfrak x_n^2,\mathfrak x_n^3):V_n\to\Omega,\qquad
\mathfrak X=(\mathfrak x^1,\mathfrak x^2,\mathfrak x^3):V\to\Omega$$
be a Nice common chart
collection, 
we denote by
$u_n=\nabla  \mathfrak x_n^1/|\nabla\mathfrak x_n^1|$.
Then 
for any
smooth function $\phi\:\Omega\to\R$
 with compact support
%$\supp \varphi \subset \Omega\cap\mathfrak X (A^\delta)$ %and $|\varphi|\le 1$
and its lifting $\psi_n=\mathfrak X_n\circ \varphi_n$
the sequence
$$\int\limits_{V_n} \l[H_n\<\nabla\psi_n,u_n\>- \<\nabla\psi_n,\nabla_{u_n} u_n\> \r]dVol_n$$
converges.
\end{thm}


\begin{thm}{Lemma}\label{Int-alm-conv}
Let
$$\mathfrak X_n=(\mathfrak x_n^1,\mathfrak x_n^2,\mathfrak x_n^3):V_n\to\Omega,\qquad
\mathfrak X=(\mathfrak x^1,\mathfrak x^2,\mathfrak x^3):V\to\Omega$$
be a Nice common chart
collection, a point $p\in V$
and
we denote by
$u_n=\nabla  \mathfrak x_n^1/|\nabla\mathfrak x_n^1|$.
Then
 there are open set $\Omega^*\ni \mathfrak X(p)$ and $c>0$ such that
  the following holds.
  
For any smooth function
$\phi\:\Omega\to\R$  with compact support
$\supp \varphi \subset \Omega^*\cap\mathfrak X (A^\delta)$ and $|\varphi|\le 1$,
we have for its lifting
 $\psi_n=\mathfrak X_n\circ \varphi_n$:

$$\limsup_{n\to\infty} \int\limits_{V_n}\Int_n\psi_ndVol_n-\liminf_{n\to\infty} \int\limits_{V_n}\Int_n\psi_ndVol_n<c \delta.$$
\end{thm}

\parit{Proof of \ref{H-converges}.}

We rewrite
$$\int\limits_{V_n} \<u_n,\nabla\psi_n\> H_ndVol_n
=
\int\limits_{V_n} \<u_n,\nabla\psi_n\> \div u_ndVol_n
$$

Let us denote by $(u^1_n, u^2_n, u^3_n)$
coordinates of $u_n$,
by $g_{ij,n}$ components of metric tensor of $M_n$ in $\Omega$ and
 rewrite the integral in $\Omega$:

$$\int\limits_{\Omega} \Bigl(\sum_{i=1}^3u_n^i \frac{\partial \phi}{\partial x_i}\Bigr)
\sum_{i=1}^3\Bigl(\partial u_n^i/ \partial x^i +u^i_n\partial \log \sqrt {\det (g_{ij,n})}/\partial x^i\Bigr)
\sqrt {\det (g_{ij,n})}dx^1\wedge dx^2\wedge dx^3$$

Now by Theorem~\ref{metricBV}
$g_{i j,n}, g^{ij}_n\in  \op{BV_0^{seq}}(\Omega,S_\Omega,\RR)$
and
$g_{ii,n}$ are bounded away from $0$.
We also have by definition  of $u_n$ that
$(u^1_n, u^2_n, u^3_n)=(1, g^{12}_n/g^{11}_n, g^{13}_n/g^{11}_n)$,
hence 
${u^i_n}\in  \op{BV_0^{seq}}(\Omega,S_\Omega,\RR)$.

Then applying
theorem~\ref{thm-D}, theorem~\ref{thm-CM}) and
theorem~\ref{thm-A} we get

\begin{itemize}

\item $\partial \log \sqrt {\det (g_{ij,n})}/\partial x^i\in \aleph_0^{seq}(\Omega,S_\Omega)$

 \item $\frac{\partial u_n^i}{\partial x_i}\in \aleph_0^{seq}(\Omega,S_\Omega)$
 
 \end{itemize} 
 
 and by above
 
  \begin{itemize}
  
  \item ${u^i_n}\in  \op{BV_0^{seq}}(\Omega,S_\Omega,\RR)\subset\op{C_0^{seq}}(\Omega,S_\Omega,\RR)$ 
 
 \item $g_{i j,n}\in   \op{BV_0^{seq}}(\Omega,S_\Omega,\RR)\subset \op{C_0^{seq}}(\Omega,S_\Omega,\RR)$
 
  \end{itemize}
  
Then applying theorem~\ref{thm-CM})
we get under integral a sum of elements from $\aleph_0^{seq}(\Omega,S_\Omega)$
multiplied by $\frac{\partial \phi}{\partial x_i}$ (which are smooth functions with compact support).
       This gives convergence of the integral by definition of  $\aleph_0^{seq}(\Omega,S_\Omega)$.
              

Further for the second integral % (see claim~\ref{cl:funDC})
we have
$$\int\limits_{M_n}\<\nabla\psi_n,\nabla_{u_n} u_n\>dVol_n=$$
 $$\int\limits_{\Omega}  \sum_{i,j,k}u^i_n \frac{\partial \phi}{\partial x_k}
 \biggl(\frac{\partial u^k_n}{\partial x_i} +\frac{1}{2}u^j_n\sum_s
 \biggl(\frac{\partial g_{ js,n}}{\partial x_i}+\frac{\partial g_{si,n}}{\partial x_j}-\frac{\partial g_{i j,n}}{\partial x_s}\biggr) g^{ks}_n\biggr)\cdot \sqrt{\op{det}(g_{i j,n})}dx^1\wedge dx^2\wedge dx^3$$ 
 
 Then as above for the first integral
 applying
theorem~\ref{thm-D}, theorem~\ref{thm-CM}) and
theorem~\ref{thm-A}  
 we  get under the integral a sum of elements from $\aleph_0^{seq}(\Omega,S_\Omega)$
  multiplied by $\frac{\partial \phi}{\partial x_i}$. Then the integral converges and the lemma follows.
  
  \qeds


\parit{Proof of \ref{Int-alm-conv}.}
We
can assume that $\mathfrak X(p)=(0,0,0)$ and here we denote by 
$B_s(O)\subset \R^2$ a ball  in coordinate $2$-plane of radius $r$ and center in the origin.
Let $R>0$, $h>0$ be sufficiently small numbers such that a cylinder 
$[-h,h]\times B_R(O)
\subset\Omega \subset\R\times\R^2$.
We want to regard level sets of functions $\mathfrak x_1$ parametrized by $\mathfrak x_2, \mathfrak x_3$
and approximate them by  level sets of  $\mathfrak x^n_1$ parametrized by $\mathfrak x^n_2, \mathfrak x^n_3$.
This level sets have a natural structure of ``admissible smoothing'', next we describe this formally.

For $s\in [0, R]$ and $t\in [-h, h]$
we denote restricted level sets by
$L^s_{t}=(\mathfrak x^1)^{-1}(t)\cap (\mathfrak x^2, \mathfrak x^3)^{-1}(B_s(O))$ and
$L^s_{t,n}=(\mathfrak x_n^1)^{-1}(t)\cap (\mathfrak x_n^2, \mathfrak x_n^3)^{-1}(B_s(O))$. 
We assume $L^R_{t}$ and $L^R_{t,n}$
to be equipped with induced intrinsic metrics while $L^s_{t}$ and $L^s_{t,n}$ with corresponding restrictions
of these metrics.




For $t\in [-h,h]$
we denote by
$\rho_t, \rho_{t,n}: B_R(O)\times B_R(O)\to\R$
 metrics pushforwarded with  maps
 $\mathfrak X|_{L^R_t}: L^R_t \to   \{t\}\times B_R(O)\xrightarrow{proj} B_R(O)$ and
 $\mathfrak X_n|_{L^R_{t,n}}: L^R_{t,n} \to   \{t\}\times B_R(O)\xrightarrow{proj} B_R(O)$
 respectively. 
 
 


Metrics $\rho_{t,n}$ comes from level sets of concave functions in manifolds with
sectional curvatures   $\ge-1$ hence by Gauss theorem theirs sectional curvatures are  $\ge-1$.
Hence $\rho_{t,n}$ are
good Riemannian
metrics on $B_R(O)$.
It can be proved the same way as in
\cite{AKP} 
(relying on \cite{petrunin-QG}, Theorem~1.2)
that 
$\rho_{t,n}$ converges to  $\rho_{t,n}$.
Hence $\rho_t$ are good Alexandrov
metrics on $B_R(O)$.
This metrics are continuous
for $t\in [-h, h]$ hence we can find unique $r>0$
such that all
these metrics have   a core $B_r(O)$. 
Then for all $t\in [-h,h]$
$L_t^r$ are  local Alexandrov spaces
$L_{t,n}^r$ are "local Riemannian manifolds".


Let $a_{t,n}: L_{t,n}^r\to L_t^r$ be identity map then    $(L_{t,n}^r, L_t^r, a_n)\in\SMA$.

%We can also assume that $\diam (B_r^{\rho_t})<1$ for all $t\in(-h,h)$. 


Now we set 
$\Omega^*=(-h, h)\times B_r(O)$,
$V_n^*=(\mathfrak X_n)^{-1}(\Omega^*)$.
Then for any smooth function $\varphi:\Omega\to\R$ with
$supp(\varphi)\subset\Omega^*$
and its lifting $\psi_n=\varphi\circ \mathfrak X_n$
we have that $supp(\psi_n)\subset V^*$
and
 we can 
rewrite
$$ \int\limits_{V_n}\Int_n(x)\psi_n(x)dVol_n(x)=\int\limits_{V_n^*}\Int_n(x)\psi_n(x)dVol_n(x)
=\int\limits_{-h}^{h} d t\int\limits_{ L_{t,n}^r}
 \frac{\psi_n(x)}{|\nabla \mathfrak x_n^1(x)|}\Int_n(x)d S_n^t(x),$$
 where $ S_n^t$ is the $2$-volume on $ L_{t,n}^r$.
 
 For any $t\in[-h,h]$ we have
  $(L_{t,n}^r, L_t^r, a_n)\in\SMA$
and Main theorem (local version ref??) for dimension $2$ can be applied.
 Hence $\Int_n(x)dS_n^t(x)$ weakly converges to some measure on $B_r(O)$.
 We also have by  Remark~\ref{rem:scPet} that
$\int\limits_{ L_t^n}
 |\Int_n(x)|dS_n^t(x)\le D$ for some $D$ independent on $t$.
 The function ${\psi_n}/{|\nabla \mathfrak x_n|}$
$c\de$-almost converges (see claims~\ref{claim:smoothgrad}, \ref{cor:scalprod}).
So for all $t\in[a,b]$ we have
$$\limsup_{n\to\infty}\int\limits_{L_t^n} \frac{\psi_n(x)}{|\nabla \mathfrak x_n^1(x)|}\Int_n(x)dS_n^t(x)-
\liminf_{n\to\infty}\int\limits_{L_t^n} \frac{\psi_n(x)}{|\nabla \mathfrak x_n^1(x)|}\Int_n(x)dS_n^t(x)
\le c D\delta.$$
\qeds

\subsection{Proof of Lemma~\ref{A^0}.}\label{sec:3dim}

In this section we 
express curvature tensor 
via Strange curvature
 to prove Lemma~\ref{A^0}.

\subsubsection {The form ${Str} Q$ associated with quadratic form $Q$ }

Given a quadratic form $Q\:\R^3\times\R^3\to\R$, we
define a quadratic form
$\Str Q:\R^3\times\R^3\to\R$ by
$$\Str Q(v,v)=2Q(v,v)+Q(v^\bot_1)+Q(v^\bot_2)=Q(v)+|v|^2\cdot\Tr Q,$$
where $v,v^\bot_1,v^\bot_2$ are mutually orthogonal and
 theirs norm equals $|v|$.
 We note that $Q$ can be reconstructed from $\Str Q$:
 $$Q(v,v)=\Str Q(v,v)-|v|^2\Tr \Str Q/4.\eqlbl{Q}$$
 \subsubsection{Vectors in general position}

We say that $6$ vectors 
 $w_1,\dots,w_6\in\R^3$ are 
  \emph{in general position}
if any quadratic form $Q:\R^3\times \R^3\to\R$
can be computed from values $Q(w_k, w_k), k=1,\dots,6.$ 
 This property depends only on the set of coordinates of this vectors
 in any basis. 
 Let us describe this formally.
 We fix a basis $e_1,e_2,e_3$ and
 denote coordinate matrix
 by $W=(w_k^i)_{i,k=1}^{3,6}\subset \R^{3\times 6}$, so
 $w_k=w_k^ie_i$  for $ k=1,\dots,6$.
  Let $A_W\in\R^{6\times 6}$ be matrix with rows 
  $((w_k^1)^2, (w_k^2)^2,(w_k^3)^2,2w_k^2w_k^3, 2w_k^1w_k^3, 2w_k^1w_k^2)$,  
  we define for any quadratic form $Q:V\times V\to\R$  columns
 $$B_Q=(Q(e_1,e_1), Q(e_2,e_2) Q(e_3, e_3), Q(e_2, e_3), Q(e_1,e_3), Q(e_1e_2))^T $$
 and $C_Q({w_1,\dots,w_6})=(Q(w_1),\dots, Q(w_6))^T$.
 Then $w_1,\dots, w_6$ are in general position iff $\det A\neq 0$; in this case we also have that
 for any $Q$ $$ B_Q=(A_W)^{-1} C_Q(w_1,\dots,w_6).\eqlbl{B=AC}$$
 Now we rewrite this in the form that we will use. For
  an array 
 $W=(w^i_k)_{i=1,k=1}^{3,6}\subset \R^3\times\R^{6}$
 of coordinates for $6$ vectors in general position 
 we define 
 correspondences $W\mapsto s_{ij}^k(W)$ for $i, j=1,2,3$, $k=1,\dots, 6$ as follows:
 $$s_{11}^k=((A_W)^{-1})_{k1} \quad s_{22}^k=((A_W)^{-1})_{k2} \quad s_{33}^k=((A_W)^{-1})_{k3}$$
 $$s_{23}^k=((A_W)^{-1})_{k4}\quad s_{13}^k=((A_W)^{-1})_{k5}\quad s_{13}^k=((A_W)^{-1})_{k6}.$$
 Then \ref{B=AC}
 can be rewriten as
$$Q(e_i,e_j)=\sum_{k=1}^{6}s_{ij}^k(W)Q(w_k^m e_m,w_k^m e_m), \quad i,j\in\{1,2,3\}.\eqlbl{Qij}$$
So we obtain the following

\begin{thm}{Lemma}\label{Sijk}
Every $s_{ij}^k$ regarded as a
function on the subset of coordinates in $\R^{3\times 6} $ in general position
is a rational function, in particular it is
locally Lipschitz.

\end{thm}


\subsubsection{Proof} 





Let us fix Nice common chart sequence
$\mathfrak X_n =(\mathfrak x^1_n, \mathfrak x^2_n,\mathfrak x^3_n):U_n\to\Omega$,
$\mathfrak X =(\mathfrak x^1, \mathfrak x^2,\mathfrak x^3):U\to\Omega$.
Let us denote coordinate frame
$e_{1n}=\nabla \mathfrak x^1_n, e_{2n}=\nabla \mathfrak x^2_n,e_{3n}=\nabla \mathfrak x^3_n$
 and $e_{1}=\nabla \mathfrak x^1, e_{2}=\nabla \mathfrak x^2,e_{3}=\nabla \mathfrak x^3$. Let
${w^*}_1,\dots,{w^*}_6\in T_pA=\R^3$ 
be vectors in general position, we
denote their coordinates ${w^*}_k={w^*}_k^ie_i$
we can choose 6 Nice sequences $f^1_n\to f^1,\dots, f^6_n\to f^6$ around $p$, such that
$\nabla f^1,\dots,\nabla f^6$ are sufficiently close to
${w^*}_1,\dots,{w^*}_6$
and
that
measures $\Str(\nabla f^k_n, \nabla f^k_n)dVol_n$ weakly $c\delta$-converges
on $V\cap A^\delta$ for $k=1,\dots,6$ (by Lemma~ \ref{Str(v,v)})
 Let us denote
$w_{kn}=\nabla_nf^k_n$ and expression
in the frame
$w_{kn}= w_{kn}^i e_{in}$,
$W_n=(w_{kn}^i)_{i,k=1}^{3,6}$.
Then
taking $U, U_n$ sufficiently
small  so that for all $y\in U_n$ coordinates
$w_{in}^k(y)\in \R^{3\times 6}$ are in a neighborhood 
of $ {w^*}_i^k\in \R^{3\times 6}$, where
corresponding functions $s_{ij}^k$ are Lipschitz (cf. Lemma~\ref{Sijk}).




%From???we obtain thatmeasures $\Str(\nabla f^k_n, \nabla f^k_n)dVol_n$ weakly $c\delta$-converges on $V\cap A^\delta$ for $k=1,\dots,6$. 
Then applying \ref{Qij} we get that 
$$\Str(e_{in},e_{jn})=\sum s_{ij}^k(W_n)\Str(w_{kn}, w_{kn})=\sum s_{ij}^k(W_n)\Str(\nabla f^k_n, \nabla f^k_n) .   $$
We know that $w_{kn}^i$ are 
$c\delta$-converging
on $V\cap A^\delta$ (\ref{ }) and $s_{ij}^k$ are Lipschitz (on the domain where applied),
hence components of Strange curvature
$\Str_n(e_{in},e_{jn})dVol_n$
 weakly $c\delta$-converges
on $V\cap A^\delta$. 

We also know that $g^{ij}_n$ are
$c\delta$ converging on $V\cap A^\delta$ hence 
$\operatorname{Tr}\Str_ndVol_n=g^{ij}_n\Str_n(e_{in},e_{jn})dVol_n$
weakly $c\delta$-converges
on $V\cap A^\delta$.

Then applying \ref{Q} we get 
$$q((w_{kn}, w_{kn})=
\Str_n(w_{kn}, w_{kn})-(\sum_{i,j=1}^3 g_{ij,n}w^i_{kn} w^j_{kn})\operatorname{Tr}\Str_n$$
 and  measures
 $q((w_{kn}, w_{kn})dVol_n$
  weakly $c\delta$-converges
on $V\cap A^\delta$.

Then applying again \ref{Qij} we get that 
$$q(e_{in},e_{jn})=\sum s_{ij}^k(W_n)q(w_{kn}, w_{kn})=\sum s_{ij}^k(W_n)q(\nabla f^k_n, \nabla f^k_n) .   $$

Then as above we can obtain that
$q((e_{in}, e_{jn})dVol_n$
  weakly $c\delta$-converges
on $V\cap A^\delta$.

Now let $f_n\ccto f$ be arbitrary $C^1_{Alex}$-converging sequence. For
decomposition $\nabla f_n =\sum \alpha^i_ne_{i,n}$,
we have that $ \alpha^i_n$
$c\delta$-converges
on $V\cap A^\delta$. Then measures
$q(\nabla f_n, \nabla f_n)dVol_n=
\sum \alpha^i_n \alpha^j_n q((e_{in}, e_{jn})dVol_n$
weakly $c\delta$-converges
on $V\cap A^\delta$.

\qeds










\section{The case when the limit space is a cone}\label{sec:cone}

Here is the proof for the case when $\omega<3\pi/2$,
we have problems with $\omega\ge 3\pi/2$.
\subsection{Limit measure tensor, sketch of the proof }

Let us denote by $\Cone_\omega$ the two-dimensional cone with total angle
 $2\cdot\pi-\omega$ and apex $p$.

In this section we consider Alexandrov space $A=\Cone_\omega\times\RR^{m-2}$
and a smoothing $M_n\smooths{} \Cone_\omega\times\RR^{m-2}$ with the
additional property, that $\sec M_n\ge -\eps_n$ for some positive $\eps_n\to 0$.
For this case we proof the version of Main theorem (Claim~\ref{CurvCone}),
 where we specify the limit curvature
measure tensor.
To formulate this statement we need some constructions that we describe roughly here,
the exact formulations are in next subsection. 

We fix orthonormal frame in the regular factor of the tangent space in the origin:
 $a_1,\dots,a_{m-2}\in\{p\}\times\R^{m-2}\subset T_p\Cone_\omega\times\RR^{m-2}
 =\Cone_\omega\times\RR^{m-2}$,  this basis can be extended to  the parallel
vector fields
$a_1(x),\dots,a_{m-2}(x)\in T_x\Cone_\omega\times\RR^{m-2}$. This vector fields
can be lifted in some natural (but non unique) way (Lemma~\ref{lem:existhoriz})
to  
vector fields
$a_{1,n}(x),\dots,a_{m-2,n}(x)\in T_xM_n$.
These vector fields define distribution on $M_n$ which is approximately
parallel to singularity, we call
vectors in this distribution "vertical" and   for any vector $v\in T_xM_n$
we denote by
$\mathring {v}$
the orthogonal projection onto this distribution
and call it "vertical part" of $v$.
It can be proved (Lemma~\ref{}) that for sequence of
convergent vector fields
$v_n: M_n\to TM_n$ 
theirs vertical parts $\mathring v_n$ converge in some sense to vertical
vector field 
$\mathring v$ on
$\Cone_\omega\times\RR^{m-2}$. The main result of this section is
the following:


\begin{thm}{Claim} \label{CurvCone}
In the above condition and notation let
$v_{1,n}, \dots, v_{m-2,n}$
be  vector fields on $M_n$ such that their vertical parts 
converge
 and
$\mathring {v}_1, \mathring {v}_2, \dots,  \mathring {v}_{m-2}$ denote
 corresponding limits of these
vertical parts. 
Then
measures
$q_{M_n}(v_{1,n}, \dots, v_{m-2,n}, v_{1,n},\dots, v_{m-2,n})\cdot dVol_n$
weakly converge
to the measure
 $$\omega\cdot|\mathring {v}_1\wedge \mathring {v}_2\wedge\dots\wedge  \mathring {v}_{m-2}|^2\cdot d\nu$$
 where $d\nu$ denotes measure that is equal to $(m-2)$-dimensional volume on $\{p\}\times\R^{m-2}\i \Cone_\omega\times\RR^{m-2}$ and vanishes outside this set.
 
  \end{thm}

It is convenient here instead of curvature form $q$ regard quadratic form
$$Q: (\Lambda^{m-2} T)M \times (\Lambda^{m-2} T)M\to\R$$ by
$Q(v_1\wedge\dots\wedge v_{m-2}, w_1\wedge\dots\wedge w_{m-2})
=q(v_1,\dots,v_{m-2},w_1\dots,w_{m-2})$.
We denote
$E_n=a_{1,n}\wedge\dots\wedge a_{m-2,n}$.

There is the two technical analytic ingredients in our prove. 
The first one is that measures
$Q(E_n, E_n)dVol_n$ weakly converge
to the measure
$\omega\cdot d\nu$. The second is that for any bounded 
continuous field $W_n: M_n\to (\Lambda^{m-2} T)M$ such that
$W_n\perp E_n$ measures
$Q(W_n, W_n)dVol_n$ weakly converges to zero measure.
Then we can deduce that
$Q(E_n, W_n)dVol_n$ weakly converges to zero measure.
This follows from the quadratic form symmetry and the fact that
every partial weak limit of
$Q(tE_n+W_n,tE_n+W_n)dVol_n$ is bounded below by zero measure,
(because of condition $\sec M_n\ge -\eps_n$).

Now we have all information about tensor $Q$. For 
sequences of
 convergent vector fields 
 $ {v}_1, {v}_2, \dots,   {v}_{m-2}$ on $M_n$ let
$V_n= {v}_1\wedge {v}_2\wedge \dots\wedge   {v}_{m-2}\in (\Lambda^{m-2} T)M$,
we can decompose $V_n=\alpha_n E_n+W_n$, where $W_n\perp E_n$.
Then
 $Q(V_n, V_n)= \alpha_n^2Q(E_n, E_n)+2\alpha_n Q(E_n, W_n)+Q(W_n, W_n)$
 and $\alpha_n\to|\mathring {v}_1\wedge \mathring {v}_2\wedge\dots\wedge  \mathring {v}_{m-2}|$. Then the claim follows.
 
 \subsection{Vertical and horizontal directions}
 
 \subsubsection{Horizontal functions}
 
 Let unit vector
$a\in \{O\}\times\R^{m-2}\subset T_pCone\times\R^{m-2}$

$$f^a(y)=\lim_{t\to+\infty}\dist_{p+ta}(y)-t$$

This function can be approximated by Perelman type functions
which become concave on every compact set.
We denote them by
$f^a_n$.

\subsubsection{Vertical and horizontal vector fields, limit projection on vertical direction }

Let us fix orthonormal frame $a_1,\dots, a_{m-2}\in \{O\}\times\R^{m-2}\subset T_pCone\times\R^{m-2}$ and let $f^{a_i}: A\to\R$, $f^{a_i}_n:M_n\to\R$ be functions defined above.


Let $w_n$ 
be a sequence of vector fields
on $M_n$.
We say that \emph{vertical parts of $w_n$ converges}
if $\<w_n, \nabla f^{a_i}_n\>$ converges to
some constant 
$\<w, a_i\>$  for all $i=1,\dots,m-2$.
In this case
we denote
$\mathring{w}=\<w, a_1\>a_1+\dots+\<w,a_{m-2}\>a_{m-2}$
and call it limit of vertical parts of $w_n$.




We call a sequence of
vector fields $w_n$ on $M_n$ \emph{vertical at infinity} if
$|w_n-(\<w_n, \nabla f^{a_1}_n\>+\dots+\<w_n,\nabla f^{a_{m-2}}_n\>)|\to 0$.

We call a sequence of
vector fields $w_n$ on $M_n$ \emph{horizontal at infinity} if
$\<w_n, \nabla f^{a_i}_n\>\to 0$ for all $i\in\{ 1,\dots,m-2\}$.


\subsubsection{Vertical functions}
 Let unit vector
$b\in T_pCone\times\{O\}\subset T_pCone\times\R^{m-2}$

$$f^b(y)=\lim_{t\to+\infty}\dist_{p+tb}(y)-t$$

This function can be approximated by Perelman type functions
which become concave on every compact set.
We denote them by
$f^b_n$.

 
 
 \subsection{Sectional curvature   vanishes in vertical directions}
 
 Let unit vector
$b\in T_pCone\times\{O\}\subset T_pCone\times\R^{m-2}$

$$f^b(y)=\lim_{t\to+\infty}\dist_{p+tb}(y)-t$$

This function can be approximated by Perelman type functions
which become concave on every compact set.
We denote them by
$f^b_n$.

We set  $u_n=\nabla f^b_n/|\nabla f^b_n|$.
Let us  denote by $\Int_n(x)$  the scalar curvature of the level set
 $(f^b_n)^{-1}(f^b_n(x))$ at $x\in  M_n$  and by
  $G_n(x)$ the Gauss curvature of  $(f^b_n)^{-1}(f^b_n(x))$ at $x$.
  Let  us define $\Sc_n^\top(v,v)=\Sc_n-2\Ric_n(v,v)$.
  Then $\Sc_n^\top(u_n, u_n)$  is the average of sectional curvature
  in 2-planes tangent to level sets $(f^b_n)^{-1}(f^b_n(x))$.
Then sectional curvature on such  2-planes  is bounded by
 $\Sc_n^\top(u_n, u_n)+o_{n\to \infty}(1)$ because
of lower curvature bound on infinity.
In the next lemma we prove that 
$\Sc_n^\top(u_n, u_n)$
vanishes at infinity around singularity near $p$.

 \begin{thm}{Lemma}
 Let $$\X_n=(\x_n^1,\x_n^2,\dots, \x_n^m):U_n\to\Omega$$
 $$\X=(\x^1,\x^2,\dots, \x^m):U_n\to\Omega$$
 be a Nice common chart
 such that $\x_n^1=f_n^b$, $\x^1=f^b$.
 There exist
 $O\in\Omega^*\subset \Omega$ and $c>0$
 such that for any $\varepsilon>0$ and 
 %continuous function $\varphi:\Omega\to\R$ with $|\varphi|\le 1$ and
 $U_n^\varepsilon=(F_n)^{-1}( \Omega^*\cap ((-\varepsilon,\varepsilon)\times\R^{m-1})  )$
  %$\supp\varphi\subset\Omega^*\cap ((-\varepsilon,\varepsilon)\times\R^{m-1})$
we have $$\limsup_{n\to\infty}\int_{U_n^\varepsilon}
| Sc_n^\top(u_n,u_n)| dVol_n\le c\varepsilon .$$
 %where $\psi_n=\varphi\circ F_n: U_n\to\R$.
 
 
\end{thm}
 \parit{Proof.}
 We can assume $\Omega$ to be of the form 
 $\Omega=(-h,h)\times B_R^{\R^{m-1}}(0)$.
 For every $t\in(-h,h)$ level set
 $L_{t}=(\x^1)^{-1}(t)$ has a structure of a good Alexandrov metric
 with a smoothing $L_{t,n}=(\x^1)^{-1}(t)$. For sufficiently small
 $r>0$ for every $t\in(-h,h)$  $L_t$ has a core $L_t^*=(\X)^{-1}(\{t\}\times B_r^{\R^{m-1}}(0))$.
 Then for $L_{t,n}^*=(\X_n)^{-1}(\{t\}\times B_r^{\R^{m-1}}(0))$
 we can write $(L_{t,n}^*,L_t^*,id_n)\in\SMA$, where $id_n$ is the inclusion.
  We take $\Omega^*= (-h,h)\times B_r^{\R^{m-1}}(0)$.
 
 By Gauss theorem we have $Sc_n^{\top}=Int_n-G_n$ and by restriction on sectional
 curvature
 $Sc_n^{\top}\ge -2(m-1)\varepsilon_n$, where $\varepsilon_n\to 0$.
   Now since $G\ge 0$
 we have
 $$ \limsup_{n\to\infty}\int_{U_n^\varepsilon}| Sc^\top(u,u)| dVol_n\le
 \limsup_{n\to\infty}\int_{U_n^\varepsilon}| Int_n| dVol_n. $$
 
 We rewrite
$$ \int_{U_n^\varepsilon}| Int_n| dVol_n =
\int_{-\varepsilon}^\varepsilon\int_{L^*_{t,n}}\frac{|Int_n|}{|\nabla \x^1_n|}dS_n,$$
where
  We can assume $r$ to be sufficiently small, so that all $L^*_{t,n}$ have diameter
  $\le 1$, then 
 for all $L_{t,n}$ Petrunin's theorem
on upper bound  of scalar curvature can be applied 
(Theorem~\ref{scPet} and Remark~\ref{rem:scPet}). Now since $|\nabla \x^1_n|>1/2$
for large $n$
we have
$$\int_{-\varepsilon}^\varepsilon\int_{L^*_{t,n}}\frac{|Int_n|}{|\nabla \x^1_n|}dS_n\le
const(m)\cdot\varepsilon$$ 
 and Lemma follows. \qeds
 
 
 
 
 \begin{thm}{ Corollary}\label{verticalK}

Let  $u_n$ be continuos bounded vertical vector fields on $M_n$ and 
$v_n$ be continuous bounded
vector fields. Then
 measures 
$K_{u_n\wedge v_n}dVol_n$
 weakly converge to $0$ measure on
 $A=\Cone_\omega\times\RR^{m-2}$.
  \end{thm}
  
  \subsection{Sectional curvature converges in horisontal directions}
 
 Let $f^a$, $f^a_n\to f^a$
 be  horizontal functions defined above, let
 $u_n=\nabla f_n/|\nabla f_n|$.
 
 \begin{thm}{Lemma}\label{horizon}
 In the above condition and notations
 $\Str_n(u_n, u_n) dVol_n$ weakly converges to some measure
 on some open $U\ni p$.
 \end{thm}
 
 Let $$\X_n=(\x_n^1,\x_n^2,\dots, \x_n^m):U_n\to\Omega$$
 $$\X=(\x^1,\x^2,\dots, \x^m):U_n\to\Omega$$
 be a Nice common chart
 such that $\x_n^1=f_n^a$, $\x^1=f^a$. 
 Then weak convergence of
 $\Str_n(u_n, u_n) dVol_n$ can be proved as 
 Lemma~\ref{lemma:maincoord} (which is reduced to Lemma~\ref{H-converges}
 and Lemma~\ref{Int-alm-conv}). 
Let note that error $c\delta$ appears only in Lemma~\ref{Int-alm-conv}
 because of $c\delta$-convergence of $1/|\nabla\x^1_n|$.
   In our case we know that $|\nabla f_n^a|=|\nabla \x^1_n|$
 converges and bounded from $0$, hence  $1/|\nabla\x^1_n|$
 converges and we obtain convergence of all integrals.
   
   \begin{thm}{Corollary}
   
   Let $a_1,\dots, a_{m-2}\in \{O\}\times\R^{m-2}\subset T_pCone\times\R^{m-2}$ be an orthonormal frame and  $f^{a_i}: A\to\R$, $f^{a_i}_n:M_n\to\R$  horizontal functions defined above. Then
   $q(\nabla f^{a_1}_n,\dots, \nabla f^{a_{m-2}}_n,\nabla f^{a_1}_n,\dots, \nabla f^{a_{m-2}}_n)dVol_n$ weakly converges on some open $U\ni p$.
   \end{thm}
   
   Follows from Lemma~\ref{horizon},
    definition of $\Str$,
   Lemma~\ref{verticalK} and boundness of Scalar curvature. \qeds
  
  
  \subsection{General case, proof of}
  
  
  Here is our main claim, the proof is in the end of this subsection.

\begin{thm}{Claim}\label{cl:vfcone}
Suppose  that lower bound of sectional
curvature of $M_n$ tends to $0$.
Let we have sequences of  vector
fields $v_n^1,\dots,v_n^{m-2}$ on $U_n$
so that theirs vertical parts
converges and corespondent limit projections
$\mathring{v}^1, \mathring{v}^2,\dots,\mathring{v}^{m-2}$
are linearly independent.
Then  $R_n(v_n^1\wedge\cdots\wedge v_n^{m-2})$
weakly converges to some signed measure
$R^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}}=\omega(x)\cdot|\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}|^2\cdot h_{m-2}$.

\end{thm}
\begin{thm}{Sublemma}\label{lemq}
Let for sequences of vectors $a_n, v_n\in V_n$ and quadratic forms $Q_n$
we have:
1)$ Q_n(a_n)\to 0$
2)$ Q_n(v_n)<C$, for some constant $C$
3) for every constant $c \liminf Q_n(c a_n+v_n)\ge 0,$
then $$\lim Q_n(a_n, v_n)=0,$$
in particular
$$\lim Q_n(c a_n+v_n)-Q_n(v_n)=0.$$
\end{thm}

\parit{Proof of \ref{cl:vfcone}}

We take lifting of ``vertical'' subspace
$V_n^\bot=Lin(\nabla f_n^{\mathring{v}^1},\dots,\nabla f_n^{\mathring{v}^{m-2}})$,
its orthogonal $V_n^\top$ and decomposition
$v_n^i=(v_n^i)^\bot+(v_n^i)^\top$.
We can regard $R_n$ as quadratic form on  $\Lambda^{m-2}(\T_x M_n)$.
Then
$$R_n((v_n^1\wedge\cdots\wedge v_n^{m-2})
=R_n((v_n^1)^\bot\wedge\cdots\wedge (v_n^{m-2})^\bot+\lambda_n^\top),$$
where  $\lambda_n^\top$ is a sum of
 simple $(m-2)$-vectors, each of those include $(v_n^i)^\top\wedge\dots$
for some $i$.
Vectors $(v_n^i)^\top$ are ``horizontal''
hence $R_n((v_n^i)^\top\wedge\dots)\to 0$ because of lemma~\ref{lem:vert} and
condition $\lim R_n\ge 0$.
 By lemma~\ref{lem:horiz}
$R_n(\nabla f_n^{\mathring{v}^1}\wedge\dots\wedge \nabla f_n^{\mathring{v}^{m-2}})$
converges, also
$|\nabla f_n^{\mathring{v}^1}\wedge\dots\wedge \nabla f_n^{\mathring{v}^{m-2}}
-(v_n^1)^\bot\wedge\cdots\wedge (v_n^{m-2})|^\bot\to 0$
hence
$R_n((v_n^1)^\bot\wedge\cdots\wedge (v_n^{m-2})^\bot)$ converges.
Now we can apply lemma~\ref{lemqq} and obtain convergence
of
$R_n((v_n^1\wedge\cdots\wedge v_n^{m-2})$.
\qeds

\subsection{Proof of details}\label{subs:prd}

\begin{thm}{Lemma}\label{lem:exost}
We can find finite set of vectors $a^i\in \Cone$
and small $c>0$ with the following property:
If $f^i$ is corresponding functions from lemma~\ref{lem:perp}
and $f^i_n$ are theirs liftings
then for every point $x\in M_n$
there are $i,j$, so that
$\angle (\nabla f^i_n(x), \nabla f^j_n(x))>c$.
\end{thm}
\begin{proof}
AP promised to write this.
\end{proof}
\begin{thm}{Lemma}\label{lem:horiz2dim}
Let $w^1_n, w^2_n$ be uniformly bounded sequences of
``horizontal'' vectors and angle between them is uniformly
bounded away from zero. Then
for every ``horizontal'' sequence $w_n$
its projection onto space orthogonal to $Lin\<w^1_n,w^2_n\>$
tends to zero. Moreover
there are two bounded sequences of coefficient
 $\alpha_n, \beta_n$ so that
$|w_n-(\alpha_n w^1_n+\beta_n w^2_n)|\to 0$.
\end{thm}
Now since sequences $\nabla f^i_n(x)$
are ``horizontal'' we can combine
Corrollary 2 (\ref{lem:0basis}), lemma~\ref{lem:exost}
and lemma~\ref{lem:horiz2dim} to obtain
lemma~\ref{lem:vert}.


\parit{Proof of \ref{lem:horiz}}
Suppose that vectors $a^1,\dots,a^{m-2}$ from lemma~\ref{lem:horiz}
are orthonormal, we choose and fix some sequences of unite vector
fields $w^1_n,w^2_n$ that are orthogonal to each other
and to $u^i_n$ for $1\le i\le m-2$.
Then
$$\Str_n(u^1_n)=2R(u^1_n\wedge\dots\wedge u^{m-2}_n)+\lambda_n+o_{n\to\infty}(1)$$
where $\lambda_n$ is the sum of items of the form
$c R(w^i\wedge\dots)$, where $c,i\in\{1,2\}$,
each of them tends to zero by lemma~\ref{lem:vert} because $w^i_n$ are ``horizontal''.
Now convergence of $\Str_n(u^1_n)$ (by sublemma~\ref{lem:strCone})
implies convergence of $R(u^1_n\wedge\dots\wedge u^{m-2}_n)$.
The case of general vectors $a^1,\dots,a^{m-2}$ can be
reduced to this one, because corespondent wedge products
coinside up to a constant.
\qeds

\section{Blow-up at $m-2$ singularity}\label{sec:blow}

Assume $M_n$ is a smoothing of Alexandrov space $A$;
i.e. $M_n$ is a non-collapsing sequence of Riemannian manifolds
with curvature $\ge\kappa$ for some $\kappa\in\RR$ and
$M_n\GHto A$.

Note that given $p\in A$,
one can allways find a sequence $\lambda_n$
which converge to infinity so slow that
$(\lambda_n M_n,p_n)\GHto \T_p A$.
In other words, $\lambda_n M_n$ is a smoothing of $\T_pA$;
further this new smoothing will be called a \emph{blow-up smoothing} at $p$.

We will use blow-up smoothg to invesigate behavior of curvature near points $p\in A'$.
In this case $\T_p\iso\Cone\times \RR^{m-2}$.






\begin{thm}{Construction}\label{constr}
Fix $\lambda_n\to\infty$. There is $\varepsilon_n\to 0$ so that

$$\GHdist(h_{\lambda_n}B^A_{R_n}(p), B^{\T_p A}_{\lambda_n R_n}(p))\le\varepsilon_n/2$$

There is a monotonic function
 $k(n)\:N\to N$
so that for every $l\ge k(n)$
$$\GHdist(h_{\lambda_n}B^{M_l}_{1}(p), B^{\T_p A}_{\lambda_n}(p))\le\varepsilon_n/2.$$

Then for every  $k'(n)\ge k(n)$ we have
$$\lambda_n M_{k'(n)}\GHto (\T_p A, p)=(\RR^{m-2}\times \Cone_x^2,x).$$
\end{thm}
For every $\lambda>0$ we supply manifold $\lambda M_n$
with vector fields
$\bar v_n^i=1/\lambda(d h_{\lambda}v_n^i)$. We will write shortly
$R_{\lambda M_n}=R_{\lambda M_n}(\bar v_n^1\wedge\dots\wedge\bar v_n^{m-2})$

\begin{thm}{Lemma}\label{l:convVCone}
Let vector field $v_n$ on $M_n$
converges with respect to Gromov--Hausdorff
convergence $M_n\GHto A$.
Fix $\lambda_n\to\infty$.
There is a monotonic function
 $k(n)\:N\to N$ so that  for every  $k'(n)\ge k(n)$
 we have that
$$\lambda_n M_{k'(n)}\GHto (\T_p A, p)=(\RR^{m-2}\times \Cone_x^2,x)$$
and
vertical parts of $\bar v_n$ converge.
\end{thm}

\begin{thm}{Claim}\label{cl:convVCone}
Let vector field $v_n$ on $M_n$
converges with respect to Gromov--Hausdorff
convergence $M_n\GHto A$.
Fix $\lambda_n\to\infty$.
There is a monotonic function
 $k(n)\:N\to N$ so that  for every  $k'(n)\ge k(n)$
 we have that
$$\lambda_n M_{k'(n)}\GHto (\T_p A, p)=(\RR^{m-2}\times \Cone_x^2,x)$$
and
$R_{\lambda_n M_{k'(n)}}$
weakly converges to $R^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}}_p$,
where $\mathring{v}^i$ are limits of vertical parts of $\bar v_n$.
\end{thm}

\parit{Proof.} By the lemma~\ref{l:convVCone} we can apply claim \ref{cl:vfcone}.
\qeds




\subsection{Proof of \ref{l:convVCone}}

Let sequence of Alexandrov spaces converges
$(N_n,p_n)\GHto (A,p)$.
 Let $A$ contains a line $\RR_a\subset A$
 with direction
$a\in \T_p A$.
We say that a sequence of points  $x_n\in N_n$
converges $x_n\GHto\RR_a^{+\infty}$ if
there are sequences $R_n\to\infty,\varepsilon_n\to 0$
so that
$$\GHdist(B^{N_n}_{R_n}(p_n), B^{A}_{R_n}(p))\le\varepsilon_n$$
and there is a sequence $t_n\to+\infty$,
so that
$t_n a\le R_n+2$ and
 for $a_n=t_n a\in \RR_a\subset A$
we have
$\GHdist(x_n,a_n)\le\varepsilon_n$.
We say that a sequence of points  $y_n\in N_n$
converges in weak sense $y_n\GHwto\RR_a^{+\infty}$ if
$|p_n y_n|\to \infty$ and
for some sequence
$x_n\GHto\RR_a^{+\infty}$ we have $\angle (x_n p_n y_n)\to 0$.

\begin{thm}{Lemma}\label{lem:angle}
Let we have two sequences $x_n, y_n\GHwto\RR_a^{+\infty}$,
and  sequence $q_n\in N_n$ is uniformly bounded, i.e. $|p_n q_n|<c$,
than $\angle (x_n q_n y_n)\to 0$.
\end{thm}




\begin{thm}{Lemma} \label{lem:vconvergLoc}
Let $M_n\GHto A$ and vector fields $v_n$ converges.
Let sequence $\lambda_n\to\infty$.
Let vector $a\in \T_p A$
and for sequences $q_s, q_s'$
we have $\angle (a,\dir{p}{q_s})<\varepsilon_s$,
 $\angle (-a,\dir{p}{q'_s})<\varepsilon_s$.
There is a  limit product $\<v,a\>$
with the following properties:
there is a constant $c>0$,
a function $k\: N\to N$,
 sequences
$M_i\ni q_{n,i}\to q_n$, $\varepsilon_n\to 0$
and
so that for   all $n$
$$\<v,a\>- c\cdot \varepsilon_n
\le
\inf_{i\ge k(n)}\inf_{x\in B_{1/\lambda_n}^{M_i}(p_i)} \< v_i,\dir{x}{q_{n,i}}\>
\le
\sup_{i\ge k(n)}\sup_{x\in B_{1/\lambda_n}^{M_i}(p_i)}  \< v_i,\dir{x}{q_{n,i}}\>\le
\<v,a\>+
 c\cdot \varepsilon_n$$
and for any function $s(n)>k(n)$
$$h_{\lambda_n}( q_{n,s(n)})\GHwto\RR_a^{+\infty}.$$

\end{thm}

\parit{Proof.}
We know, that $(\lambda_n A, p)\GHto (\T_p A, p)=(\RR^{m-2}\times \Cone_x^2,x)$.
There is a sequence $\tilde q_s, \tilde q_s' \in B_1^A(p)$,
 sequence $\tilde \varepsilon_s\to 0$, constant $c$ so that the following holds:
%$$h_{\lambda_n}(\tilde q_n)\GHwto\RR_a^{+\infty}$$
%$$h_{\lambda_n}(\tilde q_n')\GHwto\RR_{-a}^{+\infty}$$
$$\angle(a,\dir{\tilde q_s}{p})\ge\pi- \varepsilon_s/2$$
 $$\angle(\tilde q_s p\tilde q_s')\ge\pi- \varepsilon_s/2$$
and shortest paths $p\tilde q_s$, $p\tilde q_s'$ are unique.
%For any such sequences holds: for any$p^0\in B_{1/\lambda_n}(p)$we have
We can find monotonic sequence $r_s\to 0$ so that $|p\tilde q_s|/r_s\to\infty$
for any $p^0\in B_{r_s}(p)$
and for any approximating sequences
$M_i\ni q_{s,i}\to \tilde q_s$, $p^0_i\to p^0$ we have by property~\ref{convvf}
$$\limsup_{i\to\infty}  \< v_i,\dir{p_i}{\tilde q_{s,i}}\> -c\varepsilon_k\le
\liminf_{i\to\infty}  \<v_i,\dir{p^0_i}{\tilde q_{k,i}}\>\le\limsup_{i\to\infty}  \< v_i,\dir{p^0_i}{\tilde q_{k,i}}\>
\le\liminf_{i\to\infty}  \<v_i,\dir{p_i}{\tilde q_{k,i}}\> +c\varepsilon_k .
$$
We know that $$\angle(\tilde q_{t_1}p\tilde q_{t_2})\le\varepsilon_s$$ for $t_1, t_2>s$.
Hence (taking other sequences $\varepsilon_k$ and costant $c$)
we can find ``limit constant'' $\<v,a\>$ so that
 $$\<v,a\>-c\varepsilon_k\le
\liminf_{i\to\infty}
\<v_i,\dir{p^0_i}{\tilde q_{k,i}}\>\le\limsup_{i\to\infty}  \< v_i,\dir{p^0_i}{\tilde q_{k,i}}\>
\le\<v,a\> +c\varepsilon_k(*).$$

Let
$$k(n)=\max\set{t\in N}{\forall s\ge n\quad 1/\lambda_s<r_t}$$
We set $q_n:=\tilde q_{k(n)}$.
By construction $h_{\lambda_n}( q_n)\GHwto\RR_a^{+\infty}$
and the estimate $(*)$ implies that we can find appropriate function $k(n)$.
\qeds


\parit{Proof of \ref{l:convVCone}.}
We take $k(n)=\max$ of that from \ref{constr}
and lemma~\ref{lem:vconvergLoc},
sequences
$M_i\ni q_{n,i}\to q_n$ from  lemma~\ref{lem:vconvergLoc}.
Let $k'(n)\ge k(n)$.
We regard convergence
$$\lambda_n M_{k'(n)}\GHto (\T_p A, p)=(\RR^{m-2}\times \Cone_x^2,x)$$
then $y_n=h_{\lambda_n}(q_{n, k'(n)})\GHto \R_a^{+\infty} $.
Let sequence $\lambda_n M_{k'(n)}\ni x_n\to x\in \RR^{m-2}\times \Cone_x^2$.
By definition we know that
 $\<v_n,\dir{x}{y}\>=\<\bar v_n, \dir{h_{\lambda_n}(x)}{h_{\lambda_n}(y )}\>$
for any $x,y\in M_n$
hence lemma~\ref{lem:vconvergLoc} implies that
$$\<v,a\>-c\varepsilon_n\le\<\bar v_n,\dir{x_n}{y_n}\>\le\<v,a\>+c\varepsilon_n.$$
Let also regard some
$a_n\GHto \R_a^{+\infty} $ from construction of $f_a$ in \ref{???}.
By lemma \ref{lem:angle}
$\angle (a_n p_n y_n)\to 0$.
Hence
$$\<\bar v_n,\dir{x_n}{a_n}\>\to\<v,a\>.$$
\qeds

\section{Proof of claim~\ref{A'}}\label{sec:codim2}
\subsection{Locally two partitial limits approximately coinside.}
\begin{thm}{Claim}\label{cl:convLocCodim2}
Let sequence of manifolds $M_n\GHto A$,
$R_n$ weakly converges to $R^o$,
point $p\in A^{m-2}$. Then
for every  $r_n\to 0$

$(1/r_n)^{m-2}R^i(B_{r_n}(p))\to R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}}(B_{1}(p))$

\end{thm}

Before the prove we give the following general lemma:

\begin{thm}{Lemma}
Let $p $ be the measure on $K$.
Let we have convergence of Alexandrov spaces $K_i\GHto K$
  and for  any space of the sequence there is smoothing $N_{in}\to  K_i$.
Let for every $i$ measures $p_{in}$ on $N_{in}$ weakly
converge to measure $p_i$ on $K_i$.
Suppose there is a function $k(i)$ so that
for every $k'\ge k$ we
have $N_{i k'(i)}\GHto K$ and
$p_{i k'(i)}$ weakly converges to $p$ (*).
Then $p_i$ weakly converges to $p$.

\end{thm}

\parit{Proof.} Standart argument - diagonal subsequence. \qeds

 \parit{Proof of \ref{cl:convLocCodim2}.}
In our case: set $\lambda_n=1/r_n$,
for homothety $h_\lambda\:A\to \lambda A$ and measure
$p$ on $A$ we denote $p^\lambda$ the pullback (pushforward?) on  $\lambda A$.


$K={\T_p A}$, $p=R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge
\mathring{v}^{m-2}}$,  $K_i={\lambda_i A}$,
$N_{in}=\lambda_i M_n$. The function $k(i)$ is
from \ref{cl:convVCone} above.
$p_{in}={\lambda_i}^{m-2}(R_n)^{\lambda_i}$
$p_i={\lambda_i}^{m-2}(R^0)^{\lambda_i}$.
Because of \ref{cl:convVCone} condition (*) of this lemma foolfilled.

By previous lemma we obtain that
${\lambda_i}^{m-2}(R^0)^{\lambda_i}$ weakly converges to measure
$R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge
\mathring{v}^{m-2}}$.
Because measure $R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge
\mathring{v}^{m-2}}$ is special? as  it is
we have ${\lambda_i}^{m-2}(R^0)^{\lambda_i}(B_1^{\lambda_i}(p))\to R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}}(B_{1}(p))$.
Since $(R^0)^{\lambda_i}(B_1^{\lambda_i}(p))=R^0(B_{1/\lambda_i}^{M_i}(p)$
the claim follows.
\qeds

Let $R^1, R^2$ be two weak limits
of  $R(v^1_n\wedge\dots\wedge v^{m-2}_n )$.

\begin{thm}{Claim}\label{cl:R12loc}


1) Suppose $p\in A^{m-2}$ be so that $R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}}\neq 0$, i.e.
$\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}\neq 0$
Then
 $$R^1(B_{r}(p))/R^2(B_{r}(p))\xrightarrow{r\to 0} 1$$
and
$$\frac{(r_2)^{m-2}R^i(B_{r_1}(p))}{(r_1)^{m-2}R^i(B_{r_2}(p))}\xrightarrow{r_1, r_2\to 0} 1, \qquad i=1, 2,$$
in particular for sufficiently small $r>0$
we have
$$ R^i(B_{2r}(p))<2\cdot 2^{m-2}(R^i(B_r(p)),\qquad i=1, 2.$$

2) Suppose $p\in A'$ be so that $R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge \mathring{v}^{m-2}}= 0$.
Then for every $\epsilon>0$ there is $r_0>0$ so that
for $r<r_0$
$$ R_i(B_{r}(p))<\epsilon\cdot r^{m-2},\qquad i=1, 2.$$
\end{thm}

\parit{Proof.} Simple consequence of \ref{cl:convLocCodim2} \qeds

\subsection{Completion of the proof.}
The set $A'$ has $\sigma$-finite $(m-2)$ Hausdorff measure,
hence in what follows we can assume all subsets of $A'$ to
be of finite $(m-2)$ Hausdorff measure.
We subdivide $A'=A'^1\cup A'^0$, here
$$A'^1=\set{x\in A'}{R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge
\mathring{v}^{m-2}}(x)\neq 0},
\quad
A'^0=\set{x\in A'}{R_p^{\mathring{v}^1\wedge \mathring{v}^2\wedge\dots\wedge
\mathring{v}^{m-2}}(x)= 0}$$
and prove that
$R^1|_{A'^1}=R^2|_{A'^1}$ and $R^i(A'^0)=0$.

Let $K\subset A'^1$ be a measurable set.
For every $\varepsilon>0$
 by \cite[2.2.2]{federer} there exists open set $W\supset K$ with
$R^i(W)\le R^i(A)+\varepsilon$.
For every $x\in A'^1$  by claim~\ref{cl:R12loc} (1)
   we can choose $r_0(x)$ sufficiently
small
so that for $r<r_0(x)$ we have
$R_1(B_r(x))/R_2(B_r(x))=1\pm \epsilon$ and
$ R^i(B_{2r}(p))<2\cdot 2^{m-2}(R_i(B_r(p)),\qquad i=1, 2$.
The set $F=B_r(x)$ for $x\in A'^1, r<r_0(x), B_r(x)\subset W$ is
$R^i$-adequate by  \cite[2.8.7]{federer}.
So we can choose countable (disjoint?!!) subfamily $G\subset F$, such that
$$R^i(W\setminus\cup G)=0.  $$
Then obviously
we have
$$|R^1(K)-R^2(K)|\le (R^1(K)+R^2(K)+1)\epsilon,$$
this proves that $R^1|_{A'^1}=R^2|_{A'^1}$.

Let $K\subset A'^0$ be a measurable set. We know that
$R^i_-(A')=0$ than for every $\varepsilon>0$
 by \cite[2.2.2]{federer} we find open set $W\supset K$ with
$R^i_-(W)\le \varepsilon$.
For every $x\in A'^0$  by claim~\ref{cl:R12loc} (2)
   we can choose $r_0(x)$ sufficiently
small
so that for $r<r_0(x)$ we have
$ R^i(B_{r}(p))<\epsilon\cdot r^{m-2}.$
We set
$$K^{r_*}
=
\set{x\in K}{r_0(x)\le r_*\ \text{and}\  dist(x,A\setminus W)>r_* },$$
obviously
$K=\cup_{r_*}K^{r_*}$. Let $h^{m-2}(K^{r_*})=c<\infty$.
We can choose approximating covering for Hausdorff measure of $K^{r_*}$:
$$\cup_k B_{r_k}(x_k)\supset K^{r_*}, r_i<r_*\  \text{and}\
\sum_k r_k^{m-2}< c+\varepsilon,$$
then $$\sum_k (R^i B_{r_k}(x_k))<\epsilon\cdot(c+1).$$
Since
$\cup_k B_{r_k}(x_k)\subset W$ we have
$R^i(\cup_k B_{r_k}(x_k))<\epsilon\cdot(c+2)$.
Hence $R^i(K^{r_*})<\epsilon\cdot(c+3)$.

\section{Proof of claim~\ref{A''}}\label{sec:codim3}

\begin{thm} {Lemma}
There is a constant $c$, so that
$$R^i(K)\le c\cdot h_{m-2}(K)$$ for every
measurable set $K$ with $h_{m-2}(K)<\infty$.
\end{thm}

\parit{Proof.}
Follows from \cite[???]{petrunin-SC}.
\qeds

In \cite{BGP} it is proved the following
\begin{thm}{Claim}
$dim_H(A\setminus A(m-2,\de) )\le n-3$
\end{thm}
Hence $h_{m-2}(A'')=0$, the claim~\ref{A''} follows.


\newpage

\section {  APPENDIX}

\section{Gromov Hausdorf function and measure convergence}

\begin{rdef} {Definition}\label{deltaconv1}
Let $A$ be topological manifold and $D\subset A$ an open set. We say that a
sequence of
signed Radon measures $\mu_n$ on $A$
weakly $\delta$-converges to measure $\mu$ on $D$ if 
for any continuos function
$f:A\to\R$ with compact  $\supp f\subset D$ and $|f|\le 1$ we have
$\int_A fd\mu_n \to \int_A fd\mu\pm\delta$.
\end{rdef}

For the sequence of uniformly bounded measures this definition is equivalent
to the folowing.

\begin{rdef} {Definition}\label{deltaconv2}Let $U\subset A$ be an open subset. We say that  a sequence 
of measures $h_n\in C^*(A_n)$  
weakly $\delta$-converges on the set 
$U$ if for any two partial
limits
$h_1, h_2$
of $h_n$
and
$\nu=|h_1-h_2|$
we have $\nu(U)\le \delta$.

\end{rdef}

\begin{rdef} {Definition}
Let $(A_n,\rho_n)$, $(A,\rho)$ be  metric spaces,
we say that a sequence of homeomorphisms $a_n:D_n\to D$ is an approximation
if
$\rho_n(a_n^{-1}(x), a_n^{-1}(y))\to\rho (x,y)$ for all $x,y\in D$.


\end{rdef}

\begin{rdef} {Definition}Let $A_n$, $A$ be  metric spaces
$ D_n, D_n'\subset A_n$, $D\subset A$
let
$a_n: D_n\to D$ and
$a_n':D_n'\to D$ be approximations.
We say that $a_n$ is equivalent to $a_n'$ if
$\rho_n(a_n^{-1}(x), a_n'^{-1}(x))\to 0$ for all $x\in D$. 
\end{rdef}

\begin{thm}{Lemma}
Let $A_n$, $A$ be  metric spaces
$ D_n, D_n'\subset A_n$, $D\subset A$
let
$a_n: D_n\to D$ and
$a_n':D_n'\to D$ be equivalent approximations. Then
$\mu_n$ weakly $\delta$-converges to $\mu$ on $D$ w.r.t. $a_n:D_n\to D$
iff 
$\mu_n$ weakly $\delta$-converges to $\mu$ on $D$ w.r.t. $a_n':D'_n\to D$.
\end{thm}


\begin{thm}{Lemma}\label{smoothmeasure}
Let open $\Omega\subset\R^n$ and
$\mu_n$ be a  uniformly bounded sequence of signed Radon measures
on $\Omega$.
 Suppose that for any function 
$\varphi \in C^\infty(\Omega)$ with compact support and
$|\varphi|\le 1$ the sequence
 $\int_A \varphi d\mu_n$ $\delta$-converges.
 Then $\mu_n$ weakly $\delta$-converge.
\end{thm}


  \begin{rdef}{Remark}
  The condition of uniform boundness is important.
  Otherwise {\bf??}   
  \end{rdef}

\begin{rdef} {Definition}

We say that a sequence of continuous functions $f_n\: A_n\to\RR$
$\delta$-converges to a continuous function $f\:A\to\RR$
on $U\subset A$
 if supports of $f_n$ are uniformly bounded
and for any sequence of points $x_n\to x\in U$ we have that: %\nolinebreak
$\limsup f_n(x_n)+\liminf f_n(x_n)-\delta\le 2f(x)\le\limsup f_n(x_n)+\liminf f_n(x_n)+\delta.$
\end{rdef}

  
  


\section{Special functions on Alexandrov space}
\subsection{
Alexandrov-smooth functions and their level sets}
\begin{rdef}{Definitions} For an Alexandrov space $A$ we define
\emph{refinement} to be
closed sets:
$A(\delta)\subset A^{c\de}$.

%Let$B\subset A$ $f:B\to \R$.$f$ is \emph{$c$-smooth} w.r.t. the refinement $A(\de)$if $d_xf$ is $c\delta$-linear for $x\in A(\delta)$

\end{rdef}
\begin{rdef}{Addendum to definition}
\emph{$c$-Alexandrov smooth} function
%if it is $c$-smooth w.r.t. $A(\delta)=A^\delta$on a compact set.
\end{rdef}

\begin{thm}{Lemma}\label{multidelta}
1) Let
$f_1,f_2,\dots,f_l$ be $c$-Alexandrov smooth tight collection (see??)
then for $N_t=f_1^{-1}(0)\cap f_2^{-1}(0)\cap\dots\cap f^{-1}_l(0)$
we have $N_t^{c_1\delta}\supset A^\delta\cap N_t$.

2) Let $v_n$ be tangent to $N_t^n$ and $c_2\delta$-converging
on $(N^{t_0})^\delta$
for any sequence $t_n\to t_0$ w.r.t. the corresponding $GH$-convergence 
$N_{t_n}^n\GHto N_{t_n}$.
Then 
$v_n$ is $c_3\delta$-convergent 
w.r.t. the  $GH$-convergence 
$M_n\GHto A$.

\end{thm}

\begin{thm}{Claim}\label{claim:smoothgrad}
Let $f\:U\to \RR$ be smooth simple function
and $f_n$ be its lifting.
Then  gradients
$\nabla f_n$ ``converges'' for smoothing $M_n\GHto A$.
\end{thm}

Let we have   $M_n\GHto A$  a noncollapsing sequence, $\dim M_n=\dim A=m$.
\begin{thm}{Claim}\label{lem:scalprod}
Let vector fields $v_n, w_n$ ``converges'' then for every compact
set $K\subset A$ there is a constant $c>0$ so that
$\<v_n, w_n\>$ $c\de$-converges on $A^\de\cap K$.
\end{thm}
In particular we have
\begin{thm}{Corollary}\label{cor:scalprod}
Let vector fields $v_n^1,\dots, v_n^m, v_n$ be
uniformly bounded, ``converging''
 and $m$-sets of vectors
$v_n^1,\dots, v_n^m$ are uniformly linearly independent,
i.e. $\det(\<v_n^i, v_n^j\>)>c_0$
for some constant $c_0$.
Then for coefficient of decomposition
of $v_n=\alpha_n^1 v_n^1+\dots+\alpha_n^m v_n^m$
 and for every compact
set $K\subset A$ there is a constant $c>0$ so that
$\alpha_n^i$ $c\de$-converges on $A^\de\cap K$.
\end{thm}



\subsection{Properties of ``convergent''  vector fields, Equivalent definition}
\begin{thm}{Property}\label{convvf}

Let vector
field $v_n$ converges.Then for every compact $K\in A$ there is a constant $c>0$ so
that for every points $p, x, q\in K$,
%so that minimizing geodesics $[p x], [x q]$ are unique,
 and approximating sequences
 $p_n, x_n, q_n\in M_n$ so that geodesics
$[x_n q_n], [x_n p_n]$ converges to
$[x q], [x p]$ then
$$\limsup_{n\to\infty}  \< v_n,\dir{x_n}{q_n}\>-
\liminf_{n\to\infty}  \<v_n,\dir{x_n}{q_n}\>
\le $$
$$ c\cdot |x q|\cdot (\pi-\angle(p x q)).$$
\end{thm}

\parit{Proof.}
We just take function $\widetilde{\dist}_{B_r(q)}$ for
sufficiently small $r$ and  note that
$(\limsup_{n\to\infty}  |\nabla f_n(y_n)|-
\liminf_{n\to\infty}  |\nabla f_n(y_n)|)\le c(\pi-\angle(p x q))$.
\qeds



\subsection{Properties of "Alexandrov smooth" functions.}

\begin{thm}{Claim}
 Let $f_n\to f$ be a NICE Test sequence.
 Then there is a constant $c>0$,
 so that for every $x\in A^\delta$ the level set
 $L_x=f^{-1}(x)$ is $c\delta$-strained at $x$.
 
 \end{thm}
 
 
\begin{thm}{Definition}
$\delta_0$-smooth
\end{thm}



 \begin{thm}{Claim}
 Let $f_n\to f$ be a NICE Test sequence
and $g$
be an Alexandrov smooth Lipshitz
function. 
 Then there is a constant $c>0$,
 so that for every $x\in A^\delta$ 
 the restriction
 $g|_{L_x}$ to the
 the level set
 $L_x=f^{-1}(x)$ is $c\delta$-smooth at $x$
 as a function on Alexandrov space $L_x$.
 
 \end{thm}
 
 \begin{thm}{Claim}
 Let $T$ be a cone of nonnegative curvature
 and $d:T\to\R$ a concave function that is homogeneous
 on the rays.
 
 \end{thm}


\begin{thm}{Claim}\label{claim:projection}
Let vector
field $v_n$ converges.
Let $N\subset A$ be smoothable convex hypersurface
and $M_n\supset N_n\GHto N$ converging sequence of smooth convex
hypersurfaces. Then projections of vector fields $v_n^\top$ on $N_n$
converges with respect to $N_n\GHto N$.
\end{thm}
\begin{thm}{Claim}\label{claim:smoothgrad}
Let $f\:U\to \RR$ be smooth simple function
and $f_n$ be its lifting.
Then  gradients
$\nabla f_n$ ``converges'' for smoothing $M_n\GHto A$.
\end{thm}
Let we have   $M_n\GHto A$  a noncollapsing sequence, $\dim M_n=\dim A=m$.
\begin{thm}{Claim}\label{lem:scalprod}
Let vector fields $v_n, w_n$ ``converges'' then for every compact
set $K\subset A$ there is a constant $c>0$ so that
$\<v_n, w_n\>$ $c\de$-converges on $A^\de\cap K$.
\end{thm}
In particular we have
\begin{thm}{Corollary}\label{cor:scalprod}
Let vector fields $v_n^1,\dots, v_n^m, v_n$ be
uniformly bounded, ``converging''
 and $m$-sets of vectors
$v_n^1,\dots, v_n^m$ are uniformly linearly independent,
i.e. $\det(\<v_n^i, v_n^j\>)>c_0$
for some constant $c_0$.
Then for coefficient of decomposition
of $v_n=\alpha_n^1 v_n^1+\dots+\alpha_n^m v_n^m$
 and for every compact
set $K\subset A$ there is a constant $c>0$ so that
$\alpha_n^i$ $c\de$-converges on $A^\de\cap K$.
\end{thm}
\begin{thm}{Claim}
Let  $f\:U\to \RR$ be a smoothed simple concave function on
the bounded domain $U$,
$x\in U$ be a point and level
set $f^{-1}(f(x))=N$. Then there is a constant $c>0$
so that $A^\de\cap N\subset N^{\de}$.
\end{thm}


\subsection{Existence of Nice sequences and Nice tight map sequences }

Simple function $f: A\to \R$  
is a function that can be presented as
$$f=\sum_{i=1}^N \oint_{B_\varepsilon(q^i)} \phi \circ \dist_{x}dx$$
for some $q^1,\dots,q^N\in A$,  $\varepsilon>0$ 
and a concave increasing function
$\phi$.

Simple functions are 
 liftable in a natural way. Namely,
for a given sequence of Alexandrov spaces $A_n\GHto A$
 for every $q^i$ one can
   take a sequence $A_n\ni q^i_n\to q^i$
   and define
 $$f_n=\sum_{i=1}^N \oint_{B_\varepsilon(q^i_n)} \phi \circ \dist_{x}dx.$$
 
  
 \begin{thm}{Proposition}
 For any
 $p\in A$, $v\in T_pA$,
 $\varepsilon>0$
 there is a neighborhood $U\ni p$
 and a simple function 
 $$f=\sum_{i=1}^N \oint_{B_\varepsilon(q_i)} \phi \circ \dist_{x}dx$$
 such that

 1) $\sup_{x\in \cup_{i=1}^N B_\varepsilon({q_i})}\angle(\uparrow_p^x, v) $ is arbitrary
 small  and $d_pf$  is arbitrary close to $ <v,\cdot>$
 
 2) $f$ is Alexandrov smooth
 for any lifting
 1) $f, f_n$ strictly concave
 \end{thm}
 
 
 
 tight
 
 simple
 tight
 
 For any $v_1,$
 there exists Nice tight map.
 
 
 We can define lifting of this function if fix
  some lifting sequence of points $M_n\ni p_n\to p\in A$ by the same formula:
$$d_n=\widetilde{dist}_{B_r(p_n)}$$



\begin{thm}{Theorem}
For any 
$p\in A^{0.001}$
and a tight collection of %strongly linearly independent 
vectors 
$v_0, v_1,\dots,v_m$ there exists
$U\ni p$ and a Nice
tight collection of sequences
$f^0_n\to f^0, f^1_n\to f^1,\dots,f^m_n\to f^m$
with differentials $d_p f^i$
 arbitrary close to $-\<v_i,\cdot\>$.
 
 
 \end{thm}
 


\subsection{  Functions }



 \begin{rdef}{Definition}
A function $f:A\to\R$
is called a  \emph{simple function}
if there exist
 a finite set of points
$q_1, q_2,\dots,q_N\in A$
and
a $\lambda$-concave function
 $\Theta:\R^N\to\R$,
such that  
 $f=\Theta(\dist^2_{q_1},\dots,\dist^2_{q_N})$.
\end{rdef}

\begin{rdef}{Definition}
A function $f:A\to\R$
is called a  \emph{simple smooth  function}
if there are
 simple function
$\Theta(\dist^2_{q_1},\dots,\dist^2_{q_N})$
and $h>0$, such that
\begin{equation}\label{simplefun}
f=\oint_{B_h(q^1)\times B_h(q^2)\times\cdots\times B_h(q^N)} \Theta(\dist^2_{x_1},\dots,\dist^2_{x_N})dx_1dx_2\dots dx_N
\end{equation}
\end{rdef}

 
\begin{rdef}{Definition}
For a given simple smooth function $f:A\to \R$
$$f=\oint_{B_h(q^1)\times B_h(q^2)\times\cdots\times B_h(q^N)} \Theta(\dist^2_{x_1},\dots,\dist^2_{x_N})dx_1dx_2\dots dx_N.$$
and a sequence of Alexandrov spaces $A_n\GHto A$
we define
 a \emph{simple lifting} of $f$ to be a sequence of functions
$f_n:A_n\to \R$, such that there are
sequences of points $q_n^1,q_n^2,\dots,q_n^N\in A_n$,
such that
$q_n^1\to q^1, q_n^2\to q^2, \dots, q^N_n\to q^N$
and
$$f_n=\oint_{B_h(q^1_n)\times B_h(q^2_n)\times\cdots\times B_h(q^N_n)} \Theta(\dist^2_{x_1},\dots,\dist^2_{x_N})dx_1dx_2\dots dx_N.$$

\end{rdef}

\begin{rdef}{Definition}
We say that a  simple smooth function $f:A\to \R$
is Nice in $B_r(p)$ for $p\in A$ and $r>0$
 if it is strictly concave ($\lambda$-concave for $\lambda<0$),
Alexandrov smooth
on $B_r(p)$
and this two condition are open w.r.t. $GH$-convergence. Namely for any
$A_n\GHto A$, $p_n\to p$, $\varepsilon>0$ and for any simple lifting $f_n\to f$ 
for $n$ large enough $f_n$ is $\lambda+\varepsilon$-concave and
Alexandrov smooth in $B_r(p_n)$.

\end{rdef}

\begin{thm}{Existence of a Nice function}
For a given $p\in A^0$
and $v\in T_pA$ 
there exists 
a  simple smooth function $f:A\to \R$  and $r>0$
such that $f$
is Nice in $B_r(p)$
and $d_pf(\cdot)$
is sufficiently
close to $-\<v,\cdot\>$.

\end{thm}


\begin{thm}{Concave smoothing (After Green-Wu and Alexander-Kapovich-Petrunin)  }
Here we describe a $C^\infty$-smoothing in the class of $\lambda$-concave functions. 


Let us fix $r>0$ and
consider semi-concave functions $f:B_{2r}(p)\to \R$ defined on
balls in Riemannian manifolds $B_{2r}\subset M$.
There is a one-parametric (parametrized by $\varepsilon\in(0,1]$)
 family of correspondences $f\mapsto f_\varepsilon$,
where $f_\varepsilon:B_{2r}\to\R$ is a $C^\infty$ function,
with the following properties.

1) $|f-f_{\varepsilon}|(x)<C\varepsilon$, where the constant $C$ is uniform for different manyfolds and functions,
if we assume uniform bound on sectional curvatures of balls and on Lipshitz constant
for functions.

2) suppose that Riemannian metrics on $B_{2r}^{M_n}(p_n)$
$C^\infty$-converge to a Riemannian metric $B_{2r}^M(p)$ 
and $f_n$ $C^0$-converge to $f$, then

(i) $(f_n)_\varepsilon$ $C^0$ converges to $f_\varepsilon$ on $B_r^M(p)$

(ii) if $f$ and $f_n$ are $\lambda$-concave, then
$\lim_{\varepsilon\to 0} \sup_{n,\gamma} (f_n\circ \gamma)_\varepsilon ''\le \lambda$

 We
call this fixed ones and forever a correspondence $GW+AKP(\varepsilon)$-smoothing.
\end{thm}

\begin{rdef}{Definition}
Let    a simple smooth function
$f:A\to\R$ be 
 Nice in $B_{2r}(p)$,
a sequence of Riemannian manifolds $M_n\GHto A$
and $p_n\to p$.
We say that sequence of $C^\infty$ 
functions
$f_n: B_{2r}^{M_n}(p_n)\to \R$
converging to $f$
is {\emph a  Nice lifting of $f$}
if for some $\lambda<0$
 $f_n$ are $\lambda$-concave  for sufficiently large $n$.

\end{rdef}

{\bf Existence of Nice sequence} 

For any simple smooth function
$f:A\to\R$
 Nice in $B_{2r}(p)$, a sequence of Riemannian manifolds $M_n\GHto A$
and $p_n\to p$
there exists  a Nice lifting
$f_n: B_{2r}^{M_n}(p_n)\to \R$.

\parit{Construction.}
We construct
Nice lifting as follows.
Let $g_n:M_n\to \R$
be some simple
lifting  of $f$, then for some $\lambda<0$, $N>0$
 for sufficienly large $n>N$
functions $g_n$ are $\lambda$-concave. 
Then for every $n>N$ we apply to the function $f_n$
 $GW+AKP(\varepsilon)$-smoothing for $\varepsilon=\varepsilon_n$
sufficiently small, so  that $(g_n)_{\varepsilon_n}$ is
$\lambda/2$-concave and $|g_n-(g_n)_{\varepsilon_n}|< 1/n$.
Then we take $f_n=(g_n)_{\varepsilon_n}$.

\section{DC in domain of $\R^n$.}\label{sec:DC}

In this section we give simplest calculations for  a class of function sequences on domain in $\RR^m$ 
 that arise as coordinate expressions of Test sequences. 
 We follow Perelman generalizing theory (\cite{}) for sequences
 of $DC$-functions.
 
Let fix $\Omega\i \RR^m$  an open bounded domain
and
 $S_\Omega\subset\Omega\subset\R^m $ subset of
zero $(m-1)$-Hausdorff measure $h_{m-1}(S_\Omega)=0$.
%, this will be referred as a subset of {\it singularities}.


\subsubsection{Functions}
We denote by  $\op{DC_0}(\Omega,S_\Omega)$ a class of
 $\DC$-function, such  that are continuously differentiable on
$\Omega\setminus S_\Omega$.


We denote by $\op{C_0}(\Omega,S_\Omega)$ a set of bounded functions
$f\:\Omega\to\RR$, which are continuous on $\Omega\setminus S_\Omega$.


We recall that a measurable function $f\:\RR^m\to \RR$ is of
bounded variation
 ($f\in\op{BV}(\Omega,\RR)$) if there is a real constant $c$,
such that  the inequality
$$\int\limits_\Omega f\cdot D_i\phi
\le
 c\cdot\sup_{x\in\Omega}|\phi(x)|$$
holds
for any $i$ and any smooth function $\phi\:\Omega\to \RR$ with compact support.



We denote by $\op{BV_0}(\Omega,S_\Omega)$ a set of bounded functions
$f\:\Omega\to\RR$, which are continuous on $\Omega\setminus S_\Omega$.


We say that a signed Radon measure $\mu$ is in
$\aleph_0(\Omega,S_\Omega)$ if $\mu(S_\Omega)=0$.



\subsubsection{Sequences}
Let $h_n:\Omega\to\R$ be a sequence of $C^1$-differentiable $DC$-functions that
$DC$-converges to the function $h$ and in addition
$h\in \op{DC_0}(\Omega,S_\Omega)$. In this case we will write 
$$(h_n,h)\in \op{DC_0^{seq}}(\Omega,S_\Omega).$$

Let $h_n:\Omega\to\R$ be a sequence of $C^0$-functions
% with uniformly bounded supports 
that
C-converges  to the function $h$
 on
$\Omega\setminus S_\Omega$.
 %and in addition $h\in \op{C_0}(\Omega,S_\Omega)$. 
In this case we will write 
$$(h_n,h)\in \op{C_0^{seq}}(\Omega,S_\Omega).$$

Let $h_n:\Omega\to\R$ be a sequence of $C^0$-functions
with uniformly bounded variations
and  $h:\Omega\to\R$ be a 
function so that
 that $h_n$
C-converges  to the function $h$
 on the set where $h$ is continuous.
  In this case we will write 
$$(h_n,h)\in \op{CBV^{seq}}(\Omega).$$

Let $h_n:\Omega\to\R$ be a sequence of $C^0$-functions
with uniformly bounded variations
that
C-converges  to a function $h$
 on 
 $\Omega\setminus S_\Omega$.
  In this case we will write 
$$(h_n,h)\in \op{BV_0^{seq}}(\Omega,S_\Omega).$$

For  a sequence of signed Radon measure $\mu_n$
that converges weakly to the measure $\mu\in\aleph_0(\Omega,S_\Omega)$
 we will write
$$(\mu_n,\mu)\in\aleph_0^{seq}(\Omega,S_\Omega).$$


\subsubsection{Operations}
It is known that
partial derivative of $DC$ functions are of bounded variation
and the second are signed Radon measures, 
the correspondent properties for $DC$ - sequences 
are given following theorem.
\begin{thm}{Theorem}\label{thm-D}
(1) If     $( f_n, f)\in\op{DC_0^{seq}}(\Omega,S_\Omega)$ 
then for every $i$ the partial derivative (defined almost everywhere)
we have
$$\biggl(\frac{\partial f_n}{\partial x_n^i}, \frac{\partial f}{\partial x^i}\biggr)\in\op{BV_0^{seq}}(\Omega,S_\Omega).$$
(2) 
 If     $( f_n, f)\in\op{BV_0^{seq}}(\Omega,S_\Omega)$ 
then for every $i$ for the partial derivative (defined as measures)
we have
$$\biggl(\frac{\partial f_n}{\partial x_n^i}, \frac{\partial f}{\partial x^i}\biggr)\in\aleph_0^{seq}(\Omega,S_\Omega).$$

\end{thm}
We can  multiply $C_0$ functions by $\aleph_0$ measures and
obtain again $\aleph_0$ measures, the correspondent statement
for sequences is the following:
\begin{thm}{Theorem}\label{thm-CM}
Let $f_n, f\in\op{C_0^{seq}}(\Omega,S_\Omega)$,
measures $g_n, g\in\aleph_0(\Omega,S_\Omega)$,
then
$$(f_n\cdot g_n,f\cdot g)\in\aleph_0^{seq}(\Omega,S_\Omega).$$
\end{thm}
The class of $BV_0$ and $C_0$ functions and sequences is closed under analytic expression as
says the following theorem:
\begin{thm}{Theorem}\label{thm-A}
Let sequences $(f^1_n,f^1),\dots,(f^k_n, f^k) \in \op{BV_0^{seq}(C_0^{seq})}(\Omega,S_\Omega)$,
and $A$ be  $C^\infty$-function well defined in a small neighborhood of
$(f^1,\dots,f^k)(\Omega)$.
Then $$(A(f^1_n,\dots,f^k_n), A(f^1,\dots,f^k))\in\op{BV_0^{seq}(C_0^{seq})}(\Omega,S_\Omega).$$
\end{thm}


\subsection{proof dc,bv,etc.}

\parit{Proof of \ref{thm-CM}.}
We need to check that
$\int_{\Omega}f_n\cdot g_n h$ converges
for any smooth function $h$ with compact support.
Denote by $S^\delta$ the set where $f$ has jumps of size $\ge\delta$.
Since it is compact and $g(S^\delta)=0$ there exists open set
$V\supset S^\delta$ so that
 $g(clos V)<\delta$ for large $n$.
Since $f$ has no jumps of size $>\de$ on $\Omega\setminus K\supset \Omega\setminus close V$
we can find a  continuous function
$\bar f$  so that $\bar f h$ is $2\de$-close to $f h$ on
 $\Omega\setminus close V$.
Then $$\int_{\Omega}\bar f g_n h\to\int_\Omega\bar f g h$$
because $g_n$ weakly converges to $g$.
We know that $f_n h\ddto{2\de} \bar f h$ on $\Omega\setminus V$
because of compactness of $\supp f_n h\subset \supp h$,
hence $|\bar f h-f_n h|\le 4\de$ on $\Omega\setminus V$ for large $n$;
now because of uniform bound for $g_n$ we have
$$|\int_{\Omega\setminus V}\bar f g_n h-\int_{\Omega\setminus V} f_n g_n h|<C\de.$$
We also know that $g_n( V)<\delta$ for large $n$,
hence because of uniform bound for $f_n h$ we have
$$|\int_{V}\bar f g_n h-\int_V f_n g_n h|<C\de.$$
Hence $\int_{\Omega }f_n g_n h$ for every $\de>0$
$4C\de$-converges.

\parit{Proof of \ref{thm-A}.}
We can prove even more, the expression for partial derivative:
$$D_i A(f^1,\dots,f^k)=\sum \frac{\partial A}{\partial x_k}(f^1,\dots,f^k)D_if^k.$$
It is sufficient to proof for any smooth $\phi$
$$\int A(f^1,\dots,f^k)D_i\phi=\int \sum \frac{\partial A}{\partial x_k}(f^1,\dots,f^k)D_if^k\phi.$$
This equation is hold for smooth functions, then apply theorem~\ref{thm-CM}.


\section{DC-coordinates for Alexandrov space}

\subsection{Nice functions in coordinates}

A sequence of convergent convex functions in $U_n\subset M_n$ rewrited
in Nice coordinates became a sequence of $DC$-functions (difference concave).
A sequence of smooth functions  in $U_n\subset M_n$
which $C^1_{Alex}$-converges
rewrited
in Nice coordinates became a sequence of smooth functions 



Let $f_n:U_n\to\R$ be
a sequence of concave functions and
$f_n\stackrel{C}{\rightarrow}f:U\to\R$.
Then 
$(\widetilde {f_n}, \widetilde {f})\in DC(\Omega)$.

Let $f_n:U_n\to\R$ be
a sequence of smooth functions and
$f_n\stackrel{C^1_{Alex}}{\rightarrow}f:U\to\R$.
Then $\partial_i \widetilde {f}$ is correctly defined
and continuous on
$\Omega\setminus \mathfrak X(S)$
and
$\partial_i \widetilde {f_n}$
uniformly converges to
$\partial_i \widetilde {f}$
on
$\Omega\setminus \mathfrak X(S)$

for a Nice sequence
$(\widetilde {f_n}, \widetilde {f})\in DC_0(\Omega, \mathfrak X(S))$.


\subsection{Metric tensor and connection in coordinates.}\label{sec:metr-con}

\begin{thm}{Theorem}\label{metricBV}
Let
$\mathfrak X_n:U_n\to\Omega$,
$\mathfrak X:U\to\Omega$ be a Nice common chart.
Denote by $g_{ij,n}$ coordinates of metric tensor in this chart
and by $g^{ij}_n$ coordinates of the inverse matrix. 
Then
$g_{ij,n}\in BV_0^{seq}(\Omega)$
and
$g^{ij}_n\in BV_0^{seq}(\Omega)$.
In particular
$\det(g_{ij,n})$ and
$\det(g^{ij}_n)$ are bounded and bounded away from 0.

\end{thm}

\begin{thm}{Perelman's Lemma on metric tensor}\label{lem:metric-tensor}

Let $M_n\GHto A$ be a noncollapsing sequence and $\{F_n\}, F$ be a common chart.
Then
the metric tensor $g$ for chart $F$ is well defined in
$F(A^\circ)=\Omega\setminus\Omega_S $
and its components $g_{i j}$ are in $BV_0(\Omega,\Omega_S)$.

Moreover, components of  metric tensors $g_{i j, n}$  of $M_n$
regarded on $\Omega$ are $BV_0(\Omega,\Omega_S)$ converging to $g_{i j}$.
\end{thm}

Let $x_n:U_n\to\Omega$, $x:U\to\Omega$ be common smoothed
distance chart.
For any vector field
$v_n:U_n\to TU_n$  its coordinate are well defined
on $\Omega$, and for vector field $v:U\to \Omega$
its coordinate are well defined
on  $\Omega\setminus\Omega_S $, we denote this coordinates
$\widetilde{v_n^i}=dx^i_n(v_n), \quad\widetilde {v^i}=dx^i(v)$.
 
Since sequences  transition functions are $DC_0$
(and hence theirs partial derivatives are in $BV_0$) 
 it follows that if coordinates of sequence of vector fields is
in $BV$ or in $C_0$ in one smoothed distance chart,
then the same holds for another one. 

\begin{thm}{Perelman's Lemma on connection}\label{lem:connection}
Let
$A$ be Alexandrov space with singularity set
$S$,
 $\delta>0$ be sufficiently small,
 open set $U\subset A^\delta$
let $x:U\to\Omega$ be a smoothed distance chart, $S_\Omega=x(S)$
and
 $u, v, w$ be bounded vector fields on $U$,
so that $\widetilde{u^i}, \widetilde{w^i}\in\op{C_0}(\Omega,S_\Omega)$
and
$\widetilde{v^i}\in\op{BV_0}(\Omega,S_\Omega)$
then connection can be correctly defined as measure
$\langle\nabla_{u}v, w\rangle_g\in\aleph_0(\Omega,S_\Omega)$ by
the formula in coordinates:
$$\sum_{i,j,k}u^i w^j\biggl(\frac{\partial v^k}{\partial x_i}g_{k j}+\frac{1}{2}v^k\biggl(
\frac{\partial g_{i j}}{\partial x_k}+\frac{\partial g_{k j}}{\partial x_i}-\frac{\partial g_{i k}}{\partial x_j}\biggr)\biggr)\cdot \op{det}(g_{i j})^{1/2}$$ 

Furthermore, assume
we have a noncollapsing  sequence of manifolds  $M_n\GHto A$,
 and
$x_n:U_n\to\Omega$, $x:U\to\Omega$
is common smoothed
distance chart
so that $U\subset A^\delta$.
Let $u_n, v_n, w_n$ be uniformly bounded vector fields on $U_n\subset M_n$
and $u,v,w$ be limit vector fields on $U\subset A$ in a sense  
that
 $(\widetilde{u_n^i}\widetilde{u^i}), (\widetilde{w_n^i},\widetilde{w^i})\in\op{C_0^{seq}}(\Omega,S_\Omega)$
and
$(\widetilde{v_n^i},\widetilde{v^i})\in\op{BV_0^{seq}}(\Omega,S_\Omega)$,
then measures
$\langle\nabla_{u_n}v_n, w_n\rangle_{g_n}$
weakly converges to
$\langle\nabla_{u}v, w\rangle_g$ and
$$\bigl(\langle\nabla_{u_n}v_n, w_n\rangle_{g_n},\langle\nabla_{u}v, w\rangle_g\bigr)\in\aleph_0^{seq}(\Omega,S_\Omega).
$$

\end{thm}


\section{Sketch of the proof of Lemma~\ref{A^0} for higher dimensions}
We 
 prove the $c\delta$-convergence
 of co-sectional curvature 
in a small neighborhood 
for a number of $(m-2)$-collections of Test sequences,
so that a curvature tensor can be reconstructed 
as a linear combination.
So we prove firstly the convergence
for a given $(m-2)$-collection of Test sequences.

%Let a point $x_0\in A^0$ and a neighborhood $U\ni x_0 $ be sufficiently small.
We fix a tight collection of
Nice sequences of functions $g_n^1,\dots, g_n^{m-2}$    on
small converging neighborhoods $U_n$          
and regard à "foliation"  of $U^n$ into $2$-dimensional manifolds, that are
 intersections of the level sets,
 for every $t=(t_1,\dots,t_{m-2})\in (g_n^1,\dots, g_n^{m-2})(U_n)\subset\R^{m-2}$    
  we denote these manifolds by
 $K^t_n=(g_n^1)^{-1}(t_1)\cap\dots\cap (g_n^{m-2})^{-1}(t_{m-2})$
 and by $Int_n^t$ theirs intrinsic curvature. ({\bf?} 
 or sometimes  we use  notation $K_n^x$ for intersection of the level sets containing point $x\in U_n$).
 
 
 
 We know that
 $\sec K^t_n \ge\kappa$
  (see \ref{convexinconvex}) and $K_n^t \GHto K^t$(for any fixed $t$), hence 
  $K^t$ is an Alexandrov space with curvature bounded below by 
  $\kappa$ and measures with densities $Int^t_n$ w.r.t. areas
  weakly converge by Gauss-Bonnet formula to some measure on $K^t$.
  So to prove weak $c\delta$-convergence of sectional curvature 
  along $K^t_n$
   it is sufficient  
   to estimate weak $c\delta$-convergence of the
 full Gauss curvature of $K^t_n$ in $U_n$ (because of Gauss theorem).
  
  We prove this convergence in two steps:  
  
 1) We prove firstly 
 weak $c\delta$-convergence of
 determinant second  fundamental form of $K^t_n$ w.r.t. some 
 normal field.
 We denote the $3$-dimensional submanifolds
 $N^{t_2,\dots,t_{m-2}}_n=g_2^{-1}(t_2)\cap\dots\cap g_{m-2}^{-1}(t_{m-2})$, then
 by \ref{convexinconvex}  the restrictions of $g_n^1$ onto $N_n^x$ are concave   functions
 with level sets
 $K_n^x$. 
 We have by \ref{convexinconvex} 
  $\sec N^{t}_n\ge\kappa$ and
 $N_n^t\GHto N^t$, sequence $g^\#_n=g^1_n|_{N_n}$ is
 Nice {\bf (?!!)},   hence Main theorem can be applied for this sequence.
 So measures with densities  
 $R^{N_n}(\nabla g^\#_n)$ w.r.t $3$-dimensional volume
 weakly converge.
We also  know that measures with densities $Int^t_n$ w.r.t. 
$3$-dimensional volume
  weakly $c\delta$-converge (see Claim~\ref{Int-alm-conv}), hence
   applying   Gauss theorem
    we obtain  weak $c\delta$-convergence 
    for measures with densities $G^{K\subset N}$
    w.r.t.       $3$-dimensional volume.
    Let note that
    $\cdot G^{K\subset N}=\frac{1}{|w|^2}G^{K\subset U,w}$, where $w$
    is the projection of $\nabla g^1_n$ onto tangent  
    space of $N^t_n$, that is the orthogonal complement to
    $\nabla g^2_n,\dots,\nabla g^{m-2}_n$. 
    So we have weak $c\delta$-convergence 
of         the determinant of the 
second fundamental form w.r.t. normal fields $w_n$, which depends only on
gradients $\nabla g^1_n,\dots,\nabla g^{m-2}_n$. 
       
  2)We use Remark~\ref{concavelinear}
and change  linearly  $(m-2)$-collection of sequences of functions.
 By the Remark, the
    $2$-dimensional intersection sets  $K_n$
    don't change, but gradients and consequently 
     normal fields $w_n$ change linearly.
   In this way  we can prove
    $c\delta$-convergence 
of         the determinant of the 
second fundamental form for $K_n$ w.r.t.  different normal fields.     
 Finely we note that for sufficiently many (namely (m-2)(m-3)/2 {\bf?})
  normal fields in general position
  we can express the     
    full Gauss curvature of $2$-dimensional surface 
      in correspondent "relative Gauss curvatures".



\begin{thm}{Remark} \label{concavelinear}
Let 
$g_1,\dots,g_l$ be a collection of concave functions
and coefficients 
$\alpha_1,\dots,\alpha_l \ge0$, then the function
$\alpha_1g_1+\dots+\alpha_lg_l$ is concave.
Let $(\alpha_{ij})_{i,j=1}^l$ be a nondegenerate
matrix , then the intersection of all ($l$) level sets
for the collection $f_1,\dots,f_l$
coincides  
 (for appropriate parameters) with  the intersection of $l$ level sets
for the collection
 $\alpha_{11}g_1+\dots+\alpha_{1l}g_l$,\dots,  $\alpha_{l1}g_1+\dots+\alpha_{ll}g_l$.
 \end{thm}
\begin{thm}{Lemma} \label{convexinconvex}

Let 
$g_1,\dots,g_l$ be a tight collection of smooth concave functions on a Riemannian manifold $M$.
Let denote the intersection of level sets
$L_s=(g^1)^{-1}(t_1)\cap\dots\cap (g_n^{s})^{-1}(t_{s})$ for $s=1,\dots, l$,
then the restriction of
$g^{s+1}$ onto $L_s$
is a smooth concave function.  In particular
$L_{s+1}$ is a smooth 
locally convex
submanifold in $L_s$ for $s=1,\dots, l$. 
Therefore if we have lower curvature bound
$\sec M \ge\kappa$
then
$\sec L_s \ge\kappa$
for
$s=1,\dots, m-2$.
\end{thm}
\begin{thebibliography}{52}
\bibitem[AKP]{AKP} Alexander, S.; Kapovitch, V.; Petrunin A.
An optimal lower curvature bound for convex hypersurfaces in Riemannian manifolds.


\bibitem[AZ]{AZ}Aleksandrov, A.D. and Zalgaller, V.A. [1962]: Two-dimensional manifolds of bounded curvature.
Tr. Mat. Inst. Steklova 63. English transl.: Intrinsic geometry of surfaces. Trans!. Math. Monographs
15, Am. Math. Soc. (1967), Zb1.l22,170


\bibitem[BN]{BN}Berestovskij, V.N.; Nikolaev, I.G.
Multidimensional generalized Riemannian spaces. (English. Russian original)
Geometry. IV. Non-regular Riemannian geometry. Encycl. Math. Sci. 70, 168-243 (1993); translation from Itogi Nauki Tekh., Ser. Sovrem. Probl. Mat., Fundam. Napravleniya 70, 190-272 (1992).


\bibitem[BGP]{BGP} Burago, Yu.; Gromov, M.; Perelman, G., \textit{A. D. Aleksandrov spaces
with curvatures bounded below.} (Russian)  Uspekhi Mat. Nauk  47  (1992),  no.
2(284), 3--51, 222;  a bad translation in  Russian Math. Surveys  47  (1992),  no. 2, 1--58
\bibitem[Federer]{federer}Federer, H., \textit{Geometric measure theory} ???
\bibitem[OS] {OS}Otsu, Shioa

\bibitem[Per91]{PerStab} G. Perelman. \textit{Alexandrov spaces with curvatures bounded from below II. preprint}, (1991).
\bibitem[Perelman]{PerDC} G. Perelman. \textit{DC structure on Alexandrov space}

\bibitem[Petrunin-QG]{petrunin-QG} Petrunin, A., \textit{Applications of quasigeodesics
and gradient curves.}

\bibitem[Petrunin-SC]{petrunin-SC} Petrunin, A., \textit{An upper bound for curvature integral.} ???
\bibitem[Petrunin07]{petrunin-conc} Petrunin, A., \textit{Semiconcave functions in Alexandrovs geometry}




\bibitem[Reshetnyak]{Resh} \textit{ Two-dimensional manifolds of bounded curvature} // Geometry-4: Non-Regular Riemannian Geometry.  Berlin, 1993.  P. 3-163, 245-250.  (Encyclopaedia of Math. Sci.; 70). 

\bibitem[Kapovitch]{KapStab}Vitali Kapovitch \textit{Perelman's Stability Theorem.}
\end{thebibliography}
 \end{document}

Ðåøåòíÿê Þ. Ã., Äâóìåðíûå ìíîãîîáðàçèÿ îãðàíè÷åííîé êðèâèçíû, Èòîãè íàóêè è òåõíèêè. Ñîâðåìåííûå ïðîáëåìû ìàòåìàòèêè. Ôóíäàìåíòàëüíûå íàïðàâëåíèÿ. Ò. 70 (1989), 7-189.

Íàó÷íàÿ áèáëèîòåêà äèññåðòàöèé è àâòîðåôåðàòîâ disserCat http://www.dissercat.com/content/skleivanie-rimanovykh-mnogoobrazii-s-kraem#ixzz3PZY6zKdR

 
