\documentclass[a4paper,10pt]{article}
\usepackage{kusochek}

\begin{document}

\title{Curvature tensor of smoothable Alexandrov spaces}
\author{Nina Lebedeva and Anton Petrunin}
\maketitle

\input{intro.tex}
\input{prelim.tex}
\input{qc.tex}
\input{bochner.tex}
\input{almost-convergence.tex}
\input{gauss.tex}
\input{cone.tex}

\begin{thebibliography}{52}

\bibitem[AKP]{AKP} Alexander, S.; Kapovitch, V.; Petrunin A.
An optimal lower curvature bound for convex hypersurfaces in Riemannian manifolds.


\bibitem[AZ]{AZ}Aleksandrov, A.D. and Zalgaller, V.A. [1962]: Two-dimensional manifolds of bounded curvature.
Tr. Mat. Inst. Steklova 63. English transl.: Intrinsic geometry of surfaces. Transl. Math. Monographs
15, Am. Math. Soc. (1967), Zb1.l22,170


\bibitem[BN]{BN}Berestovskij, V.N.; Nikolaev, I.G.
Multidimensional generalized Riemannian spaces. (English. Russian original)
Geometry. IV. Non-regular Riemannian geometry. Encycl. Math. Sci. 70, 168-243 (1993); translation from Itogi Nauki Tekh., Ser. Sovrem. Probl. Mat., Fundam. Napravleniya 70, 190-272 (1992).


\bibitem[BGP]{BGP} Burago, Yu.; Gromov, M.; Perelman, G., \textit{A. D. Aleksandrov spaces
with curvatures bounded below.} (Russian)  Uspekhi Mat. Nauk  47  (1992),  no.
2(284), 3--51, 222;  a bad translation in  Russian Math. Surveys  47  (1992),  no. 2, 1--58

\bibitem[Federer]{federer}Federer, H., \textit{Geometric measure theory} ???

\bibitem[LM]{lawson-michelsohn} Lawson, H. Blaine, and Marie-Louise Michelsohn. \emph{Spin geometry}, 1989.

\bibitem[LS]{LS} Lange, Christian; Stadler, Stephan
Affine functions on Alexandrov spaces. 
Math. Z. 289 (2018), no. 1-2, 455–-469. 

\bibitem[OS] {OS}Otsu, Shioa

\bibitem[Per91]{PerStab} G. Perelman. \textit{Alexandrov spaces with curvatures bounded from below II. preprint}, (1991).
\bibitem[Perelman]{PerDC} G. Perelman. \textit{DC structure on Alexandrov space}

\bibitem[Petrunin-QG]{petrunin-QG} Petrunin, A., \textit{Applications of quasigeodesics
and gradient curves.}

\bibitem[Petrunin-GC]{petrunin-GC} Petrunin, A. \textit{Applications of quasigeodesics and gradient curves.} Comparison geometry (Berkeley, CA, 1993–94), 203--219, Math. Sci. Res. Inst. Publ., 30, Cambridge Univ. Press, Cambridge, 1997.

\bibitem[Petrunin-SC]{petrunin-SC} Petrunin, A., \textit{An upper bound for curvature integral.} ???

\bibitem[Petrunin07]{petrunin-conc} Petrunin, A., \textit{Semiconcave functions in Alexandrov's geometry}

\bibitem[Reshetnyak]{Resh} \textit{ Two-dimensional manifolds of bounded curvature} // Geometry-4: Non-Regular Riemannian Geometry. Berlin, 1993. P. 3-163, 245-250. (Encyclopaedia of Math. Sci.; 70). 

\bibitem[Kapovitch]{KapStab}Vitali Kapovitch \textit{Perelman's Stability Theorem.}

\bibitem[Nepechiy]{Nepechiy} Artem Nepechiy \textit{Toward canonical convex functions in Alexandrov spaces.} arXiv:1910.00253v1 [math.DG].
\end{thebibliography}
\end{document}
