\begin{thebibliography}{52}

\bibitem[AKP-2019]{AKP} Alexander, S.; Kapovitch, V.; Petrunin, A.
Alexandrov geometry: preliminary version no. 1

\bibitem[AKP-2008]{AKP-buyalo} Alexander, S.; Kapovitch, V.; Petrunin, A.
An optimal lower curvature bound for convex hypersurfaces in Riemannian manifolds.
Illinois J. Math. 52 (2008), no. 3, 1031--1033.

\bibitem[AZ]{AZ}Aleksandrov, A.D. and Zalgaller, V.A. [1962]: Two-dimensional manifolds of bounded curvature.
Tr. Mat. Inst. Steklova 63. English transl.: Intrinsic geometry of surfaces. Trans!. Math. Monographs
15, Am. Math. Soc. (1967), Zb1.l22,170


\bibitem[BN]{BN}Berestovskij, V.N.; Nikolaev, I.G.
Multidimensional generalized Riemannian spaces. (English. Russian original)
Geometry. IV. Non-regular Riemannian geometry. Encycl. Math. Sci. 70, 168-243 (1993); translation from Itogi Nauki Tekh., Ser. Sovrem. Probl. Mat., Fundam. Napravleniya 70, 190-272 (1992).


\bibitem[BNS]{BNS} Elia Bruè and Aaron Naber and Daniele Semola, Boundary regularity and stability for spaces with Ricci bounded below, 


\bibitem[BGP]{BGP} Burago, Yu.; Gromov, M.; Perelman, G., \textit{A. D. Aleksandrov spaces
with curvatures bounded below.} (Russian)  Uspekhi Mat. Nauk  47  (1992),  no.
2(284), 3--51, 222;   translation in  Russian Math. Surveys  47  (1992),  no. 2, 1--58
\bibitem[Federer]{federer}
Federer, Herbert (1969), \textit{Geometric measure theory}, series Die Grundlehren der mathematischen Wissenschaften, Band 153, New York: Springer-Verlag New York Inc., pp. xiv+676, ISBN 978-3-540-60656-7, MR 0257325

\bibitem[G]{G}
Nicola Gigli,
Riemann curvature tensor on RCD spaces and possible applications https://arxiv.org/pdf/1902.02282.pdf

\bibitem[G1]{G1}
Nicola Gigli,
Non-smooth differential geometry, to appear on Mem. Amer. Math. Soc..
Preprint, arXiv:1407.0809, 2014.

\bibitem[GMS]{GMS}
Nicola Gigli ? Andrea Mondino ? Giuseppe Savar´e ?
Convergence of pointed non-compact metric measure spaces
and stability of Ricci curvature bounds and heat flows



\bibitem[H]{H} Bang-Xian Han, 
Ricci tensor on $RCD^*(K, N)$ spaces.

\bibitem[Kap]{KapStab} Kapovitch, Vitali Perelman's stability theorem. Surveys in differential geometry. Vol. XI, 103–136, Surv. Differ. Geom., 11, Int. Press, Somerville, MA, 2007.

\bibitem[LawMich]{lawson-michelsohn}Lawson, H. and Michelsohn, M.
\textit{Spin geometry}

\bibitem[LN]{li-naber}
Li, Nan; Naber, Aaron
Quantitative estimates on the singular sets of Alexandrov spaces. 
Peking Math. J. 3 (2020), no. 2, 203--234.

\bibitem[L] {L} John Lott,\textit{
Ricci measure for some singular Riemannian metrics}
Math. Ann. (2016) 365:449-471.

\bibitem[N]{Nepechiy} Artem Nepechiy,
Toward canonical convex functions in Alexandrov spaces, 
2019,
\texttt{arXiv:1910.00253 [math.DG]},.

\bibitem[OS] {OS}   Otsu, Y.,  Shioya, T. (1994)
The Riemannian structure of Alexandrov spaces. Journal of Differential Geometry, 39(3), 629-658

\bibitem[Per91]{PerStab} G. Perelman. \textit{Alexandrov spaces with curvatures bounded from below II. preprint}, (1991).

\bibitem[Per93]{PerMorse}
Perelman, G. Ya.
Elements of Morse theory on Aleksandrov spaces.
St. Petersburg Math. J. 5 (1994), no. 1, 205–213 

\bibitem[PerDC]{PerDC} G. Perelman. \textit{DC structure on Alexandrov space}

\bibitem[Pet-QG]{petrunin-QG} Petrunin, A., \textit{Applications of quasigeodesics
and gradient curves.}

\bibitem[Pet-SC]{petrunin-SC} Petrunin, A., \textit{An upper bound for curvature integral.} April 2009St Petersburg Mathematical Journal 20(2):255-265

\bibitem[Pet-Conc]{petrunin-conc} Petrunin, A., \textit{Semiconcave functions in Alexandrov's geometry}

\end{thebibliography}
